### 2015-11-07 latex/assignment_3.tex
Added the Latex of the update in a folder

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[paper=a4, fontsize=11pt]{scrartcl} % A4 paper and 11pt font size

\usepackage[T1]{fontenc} % Use 8-bit encoding that has 256 glyphs
\usepackage{fourier} % Use the Adobe Utopia font for the document - comment this line to return to the LaTeX default
\usepackage[english]{babel} % English language/hyphenation
\usepackage{amsmath,amsfonts,amsthm} % Math packages

\usepackage{lipsum} % Used for inserting dummy 'Lorem ipsum' text into the template

\usepackage{sectsty} % Allows customizing section commands
\allsectionsfont{\centering \normalfont\scshape} % Make all sections centered, the default font and small caps
\usepackage{graphicx}
\usepackage{fancyhdr} % Custom headers and footers
\pagestyle{fancyplain} % Makes all pages in the document conform to the custom headers and footers
\fancyhead{} % No page header - if you want one, create it in the same way as the footers below
\fancyfoot[L]{} % Empty left footer
\fancyfoot[C]{} % Empty center footer
\fancyfoot[R]{\thepage} % Page numbering for right footer
\renewcommand{\headrulewidth}{0pt} % Remove header underlines
\renewcommand{\footrulewidth}{0pt} % Remove footer underlines
\setlength{\headheight}{13.6pt} % Customize the height of the header

\numberwithin{equation}{section} 
\numberwithin{figure}{section} 
\numberwithin{table}{section}

\setlength\parindent{0pt}

%----------------------------------------------------------------------------------------
%	TITLE SECTION
%----------------------------------------------------------------------------------------

\newcommand{\horrule}[1]{\rule{\linewidth}{#1}}

\title{	
\normalfont \normalsize 
\textsc{Harvard University} \\[25pt]
\textsc{CS281} \\[25pt]
\horrule{0.5pt} \\[0.4cm] 
\huge Final Project Update: \\
\huge Classification for the Yelp Data Set Challenge
\horrule{2pt} \\[0.5cm]
}

\author{Nicolas Drizard \& Virgile Audi}

\date{\normalsize\today} 
\begin{document}

\maketitle

\section{Abstract Draft}

\section{Numerical processing and first clustering experiments}

\section{Text preprocessing and LDA}
\subsection{Text preprocessing}
An important part of these first days of work was processing the text reviews on which we would perform LDA. The reviews came in the form of json file with information such as:
\begin{itemize}
\item the business id of the business reviewed,
\item the reviewer's id,
\item the number of stars given
\item the text of the review itself in the form of a string
\item and some extra information such as the class of review (fun,useful and others) based on Yelp users' votes.
\end{itemize}

We were first interested in extracting the business ids and the text reviews. The length of the texts varied a lot. Inspecting the data, we can find reviews of a line only and reviews much longer. Our motivation for this project is to classify the venues based on the text reviews, so the identity of the reviewers does not matter. We therefore merged the reviews by venues. We reduced the 1.6 million reviews to a corpus of 60785 larger texts, 1 per business. Note that we first had to clean the texts by removing capital letters, digits, etc... \\

As LDA uses the bag-of-words assumption, we only wanted to keep words that had a semantic interest. So we removed a list of stop words based on the most common words in the English language such as: "is, a, I, 'm, 's, and, can, be, etc...". This yield a total vocabulary of over 400 thousands unique words, which dazzled us at first, but we'll come back on that issue later. We then transformed the corpus into a sparse matrix for which each row corresponds to a document and column $j$ tracks the count of the word indexed by $j$ in the vocabulary. This step made our computers' ipython kernel crash multiple time but we finally obtained a sparse matrix of size 140 GB.\\

The size of the document-term frequency (dtf) matrix being too big to work with, we decided to focus only on restaurant type of businesses (the yelp data set contains reviews about dentists, supermarkets, etc.). Reprocessing everything yielded a corpus of about 18000 venues, and a total vocabulary of 200 000 words. Reevaluating the dtf matrix was then much easier. We then persued to fit a baseline LDA model using the lda 1.0.2 python package. But the computation ended up being way to expensive timewise (we left the algorithm run for 8 hours and still didn't converge even though we enforced a maximum number of iterations of 1500!). In order to show some results for this update, we subsambled 500 restaurants and ran the algorithm again. Subsampling had for consequence to reduce the size of the vocabulary to only $\sim$40 000 words. Completion time for the algorithm was about an hour for 50 topics. Some of the results are shown below:

\begin{figure}[h!]
\centering
\includegraphics[width=1\textwidth]{first_topics.png}
\end{figure}

The topics obtained a very poor and there are numerous reasons for that. The first is that we didn't get the chance to cross-validate the number of topics queried. The second is that we then noticed that we had an issue, that might result to be very problematic, with spelling. If any of the TFs have suggestions on how to tackle this issue, we would greatly appreciate it. A third reason might lie in the fact that we are failing to distinguish what constitutes the reviewer's opinion (is it good restaurant? is it bad?) and what is this restaurant about (Italian? Japanese?). This third reason motivated the analysis of a customed LDA model that we will describe below. We haven't yet done any type of analysis but this is the model that we will now focus on and code up. This will alow us to use the regular LDA as a baseline to compare new topics.\\

\subsection{The custom LDA model}

The assumption that we will make for this model is the following: each review can be divided into two parts,
\begin{itemize}
\item words coming from an opinion topic that correspond to the rating of the review (in this particular case, we will use 5 topics for 5 stars),
\item and words coming from any type of content topics.
\end{itemize}
For simplicity reason, we will also assume that the proportion of words from each part is fixed, for instance 30:70 or 40:60. Depending on the performance of this new method, we might decide to relax this last assumption and try to learn this parameter as well.\\

The new generative process for each review $r$ will therefore be:
\begin{enumerate}
\item Generate the length using a Poisson distribution: $N_r \sim \text{Poisson}(\xi)$
\item Choose an opinion topic: $o_r \sim \text{Cat}(\beta)$, where $\beta \in \mathbb{R}^5$ 
\item Draw the per-document content topic distribution: $c_r\sim \text{Dir}(\alpha)$
\item For each word $w_{ri}$,\quad generate $u \sim \text{Unif}(0,1)$:
	\begin{enumerate}
	\item If $u<=p$ where p is the fixed proportion ruling the opinion/content separation then:
		\begin{itemize}
		\item Pick a word $p(w_{ri} | o_r) \sim \text{Cat}(o_r)$
		\end{itemize}
	\item If $u>p$ then:
		\begin{itemize}
		\item Choose a latent content topic: $z_i \sim \text{Cat}(c_r)$
		\item Choose a word $p(w_{ri} | z_n) \sim \text{Cat}(z_n)$
		\end{itemize}
	\end{enumerate}
\end{enumerate}
The mathematics behind shouldn't be too different from the derivations in the regular LDA model. We shall investigate this new model in the next few days.
\end{document}

### 2015-11-07 latex/assignment_3.tex
updates with numerical processing

@@
 \date{\normalsize\today} 
+\usepackage{float}
+\floatplacement{figure}{H} % force figures to be placed always at defined position!
+
 \begin{document}
@@
 
+\subsection{Numerical Feature Extraction}
+
+This part works with two tables of the Yelp data: business and checkin.
+The first one stores information about the business (localizations, name, categories ...) and the second contains the average number of customers checkins for each hour of the week.\\
+
+We joined and converted these two tables in order to have only numerical or binary features and applied different operations:
+\begin{itemize}
+	\item Dropping irelevant features
+	\item Identifying categorical features and converting them into orthogonal vectors of a N dimensional space, with  \textit{N = number of categories}
+	\item One attribute of each business stores different information in an unstructured way (each business does not have the same number of information stored by this attribute).
+It  represents, for instance, the price, the ambience, if alcohol is offered...
+We needed to identify the most shared informations to avoid too many missing values
+\end{itemize}
+On top of these steps, we chosed to focus first on the restaurants (the yelp data set contains reviews about dentists, supermarkets, etc.).
+Also to build easily our first baselines we chosed not to handle the missing values and droped the business with not enough information.\\
+
+The result is the data set of the Yelp restaurants with 205 features relatives to the customers checkins and the inherent properties of the restaurants.
+We will test these features under supervised learning algorithms.\\
+
+Some improvement might be considered:
+\begin{itemize}
+	\item Combining features and/or applying them polynomial or cosinus base function to increase their complexity
+	\item Considering more attributes and the business where we don't have the checkin information while filling the missing values.
+This inference can be done through the average or median values over the entire data set, or through a nearest neighbors estimation.
+\end{itemize}
+
+\subsection{Supervised Learning}
+
+Considering the data set built with the processing with numerical features. We applied a multiclass logistic regression from scikit learn. \\
+
+The first question was to narrow down our targets.
+In the restaurants entries, there are still 261 different categories shared.
+As the text mining of the reviews seemed more complicated, we needed to consider the most diffenriating categories to have decent models.
+As a result, we focused on the nationality of the food to test among the restaurants.\\
+
+With 3 classes: 1 without specific nationality and the two most represented nationalities, Mexican and Chinese, the multiclass logistic regression provided poor results on the test set (the data set was separated in the schema 80:20, train:test), only slightly better than predicting no nationality for each entry (dummy model).
+The explanations could be that the features do not contain relevant information to differentiate the style and the restaurant set without missing values contains only 13000 entries with around 1000 positive for the two classes.\\\\
+Precision score:
+\begin{align*}
+	\rho_{dummy} & = 0.671423029551 \\
+	\rho_{logreg} &  = 0.726111608768 
+\end{align*}
+
+\begin{figure}[H]
+	\includegraphics[scale=0.45]{ROC.png}
+	\centering
+	\title{Multi class ROC curve}
+\end{figure}
+
+\subsection{Next steps}
+
+Given the poor results of this part, we will focus on building a strong LDA for the next steps to model the categories of the restaurant.
+These new features could then be refined with the numerical features built.
+
 \section{Text preprocessing and LDA}
 \subsection{Text preprocessing}
-An important part of these first days of work was processing the text reviews on which we would perform LDA. The reviews came in the form of json file with information such as:
-\begin{itemize}
-\item the business id of the business reviewed,
-\item the reviewer's id,
-\item the number of stars given
-\item the text of the review itself in the form of a string
-\item and some extra information such as the class of review (fun,useful and others) based on Yelp users' votes.
-\end{itemize}
+An important part of these first days of work was processing the text reviews on which we would perform LDA.
+The reviews came in the form of json file with each text review associated to a business id.\\
 
-We were first interested in extracting the business ids and the text reviews.
-The length of the texts varied a lot.
 Inspecting the data, we can find reviews of a line only and reviews much longer.
@@
 
-The size of the document-term frequency (dtf) matrix being too big to work with, we decided to focus only on restaurant type of businesses (the yelp data set contains reviews about dentists, supermarkets, etc.).
+Following the choice in the numerical feature processing, we focused only on restaurants .
 Reprocessing everything yielded a corpus of about 18000 venues, and a total vocabulary of 200 000 words.
-Reevaluating the dtf matrix was then much easier.
 We then persued to fit a baseline LDA model using the lda 1.0.2 python package.
-But the computation ended up being way to expensive timewise (we left the algorithm run for 8 hours and still didn't converge even though we enforced a maximum number of iterations of 1500!).
-In order to show some results for this update, we subsambled 500 restaurants and ran the algorithm again.
-Subsampling had for consequence to reduce the size of the vocabulary to only $\sim$40 000 words.
+But the computation ended up being way to expensive timewise ( > 8 hours).
+We subsambled 500 restaurants, which reduced the size of the vocabulary to only $\sim$40 000 words and ran the algorithm again.
 Completion time for the algorithm was about an hour for 50 topics.
@@
 
-The topics obtained a very poor and there are numerous reasons for that.
+The topics obtained are very poor and there are numerous reasons for that.
 The first is that we didn't get the chance to cross-validate the number of topics queried.
-The second is that we then noticed that we had an issue, that might result to be very problematic, with spelling.
+The second is that we then noticed that we had an issue with the spelling.
 If any of the TFs have suggestions on how to tackle this issue, we would greatly appreciate it.

### 2015-11-07 latex/assignment_3.tex
Some corrections + abstract

@@
 \textsc{CS281} \\[25pt]
-\horrule{0.5pt} \\[0.4cm] 
+\horrule{0.5pt} \\[0.1cm] 
 \huge Final Project Update: \\
@@
 
+Our objective is to improve the categorization system of the Yelp businesses using machine learning techniques.
+To achieve our goal, we will extract significant information out of the text reviews posted on Yelp using a semi-supervised Latent Dirichlet Allocation model.
+We will then combine these results with characteristic features of the business - such as localizations, price, customer type, check-in data - and predict the categories with two approaches: a classification with a Multinomial Logistic Regression and a clustering method with a K-Nearest Neighbors.
+We will provide a way to assess the quality of our new categories.
+On one hand, we will validate existing categories by holding out a set a venues, perform predictions and compare with the existing manually-entered categories.
+On the other hand, we will assess the performance of the LDA model using the perplexity metric.
+
 \section{Numerical processing and first clustering experiments}
@@
 
-This part works with two tables of the Yelp data: business and checkin.
-The first one stores information about the business (localizations, name, categories ...) and the second contains the average number of customers checkins for each hour of the week.\\
+This part focuses on two tables from the Yelp data: business and checkin.
+The first one stores information about the businesses (localizations, name, categories ...) and the second contains the average number of customers checkins for each hour of the week.\\
 
@@
 
-The result is the data set of the Yelp restaurants with 205 features relatives to the customers checkins and the inherent properties of the restaurants.
+We therefore reformatted and sampled the original data set to form a new one with 205 features relatives to the customers checkins and the inherent properties of the restaurants.
 We will test these features under supervised learning algorithms.\\
 
-Some improvement might be considered:
+Some improvements still need to be addressed:
 \begin{itemize}
@@
 
-Considering the data set built with the processing with numerical features. We applied a multiclass logistic regression from scikit learn. \\
-
+We applied a multiclass logistic regression from scikit learn as one of our baselines.
 The first question was to narrow down our targets.
@@
 With 3 classes: 1 without specific nationality and the two most represented nationalities, Mexican and Chinese, the multiclass logistic regression provided poor results on the test set (the data set was separated in the schema 80:20, train:test), only slightly better than predicting no nationality for each entry (dummy model).
-The explanations could be that the features do not contain relevant information to differentiate the style and the restaurant set without missing values contains only 13000 entries with around 1000 positive for the two classes.\\\\
+Some explanations could lie in that the features do not contain relevant information to differentiate the style and the restaurant set without missing values contains only 13000 entries with around 1000 positive for the two classes.\\\\
 Precision score:
@@
 \begin{figure}[H]
-	\includegraphics[scale=0.45]{ROC.png}
+	\includegraphics[scale=0.35]{ROC.png}
 	\centering
-	\title{Multi class ROC curve}
 \end{figure}
@@
 \subsection{Text preprocessing}
-An important part of these first days of work was processing the text reviews on which we would perform LDA.
-The reviews came in the form of json file with each text review associated to a business id.\\
-
+ The reviews came in the form of json file with each text review associated to a business id.
 Inspecting the data, we can find reviews of a line only and reviews much longer.
@@
 As LDA uses the bag-of-words assumption, we only wanted to keep words that had a semantic interest.
-So we removed a list of stop words based on the most common words in the English language such as: "is, a, I, 'm, 's, and, can, be, etc...".
-This yield a total vocabulary of over 400 thousands unique words, which dazzled us at first, but we'll come back on that issue later.
+So we removed a list of stop words based on the most common words in the English language yielding a total vocabulary of over 400 thousands unique words.
 We then transformed the corpus into a sparse matrix for which each row corresponds to a document and column $j$ tracks the count of the word indexed by $j$ in the vocabulary.
-This step made our computers' ipython kernel crash multiple time but we finally obtained a sparse matrix of size 140 GB.\\
+This step made our computers' ipython kernel crash multiple time but we finally obtained a sparse matrix of size 1 GB.\\
 
-Following the choice in the numerical feature processing, we focused only on restaurants .
+Following the choice in the numerical feature processing, we focused only on restaurants.
 Reprocessing everything yielded a corpus of about 18000 venues, and a total vocabulary of 200 000 words.
-We then persued to fit a baseline LDA model using the lda 1.0.2 python package.
+We then persued to fit a baseline LDA model using the lda python package.
 But the computation ended up being way to expensive timewise ( > 8 hours).
@@
 \centering
-\includegraphics[width=1\textwidth]{first_topics.png}
+\includegraphics[width=0.7\textwidth]{first_topics.png}
 \end{figure}

### 2015-12-03 latex/poster_parts.tex
posters parts

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[paper=a4, fontsize=11pt]{scrartcl} % A4 paper and 11pt font size

\usepackage[T1]{fontenc} % Use 8-bit encoding that has 256 glyphs
\usepackage{fourier} % Use the Adobe Utopia font for the document - comment this line to return to the LaTeX default
\usepackage[english]{babel} % English language/hyphenation
\usepackage{amsmath,amsfonts,amsthm} % Math packages

\usepackage{lipsum} % Used for inserting dummy 'Lorem ipsum' text into the template

\usepackage{sectsty} % Allows customizing section commands
\allsectionsfont{\centering \normalfont\scshape} % Make all sections centered, the default font and small caps
\usepackage{graphicx}
\usepackage{fancyhdr} % Custom headers and footers
\pagestyle{fancyplain} % Makes all pages in the document conform to the custom headers and footers
\fancyhead{} % No page header - if you want one, create it in the same way as the footers below
\fancyfoot[L]{} % Empty left footer
\fancyfoot[C]{} % Empty center footer
\fancyfoot[R]{\thepage} % Page numbering for right footer
\renewcommand{\headrulewidth}{0pt} % Remove header underlines
\renewcommand{\footrulewidth}{0pt} % Remove footer underlines
\setlength{\headheight}{13.6pt} % Customize the height of the header

\numberwithin{equation}{section} 
\numberwithin{figure}{section} 
\numberwithin{table}{section}

\setlength\parindent{0pt}

%----------------------------------------------------------------------------------------
%	TITLE SECTION
%----------------------------------------------------------------------------------------

\newcommand{\horrule}[1]{\rule{\linewidth}{#1}}

\title{	
\normalfont \normalsize 
\textsc{Harvard University} \\[25pt]
\textsc{CS281} \\[25pt]
\horrule{0.5pt} \\[0.1cm] 
\huge Final Project Update: \\
\huge Classification for the Yelp Data Set Challenge
\horrule{2pt} \\[0.5cm]
}

\author{Nicolas Drizard \& Virgile Audi}

\date{\normalsize\today} 
\usepackage{float}
\floatplacement{figure}{H} % force figures to be placed always at defined position!

\begin{document}

\maketitle

\section{Data}

We are taking part in the Yelp Dataset challenge round 6. We chosed to solve the question of infering categories based on the reviews. The goal is to build a finer way to categorize the Yelp businesses. The global question is the following: How much information can reviews give us on the type of restaurants?\\

Right now, the users define the label of each entry. This project could be used as an automation tool for Yelp to label properly its data based on the cluster we will find. This would improve the user experience while querying for a specific kind of restaurants.

Data:
\begin{itemize}
		\item 1.6 million reviews
		\item 61 000 businesses
		\item 481 000 attributes (ie hours, parking availabity, take-out, ambience)
		\item aggregated check-in measurements over time
\end{itemize}

We focused first on the restaurants and for one city at a time to grasp in a finer way the local relationships of the restaurants. This also makes more sense on from the user's perspective.\\

\section{Approach}

Our main goal is to build latent features from the text reviews which would depict the categories of the business. To put it in a nutshell, we would like to build from the text reviews of an entry a vector representation which carries local geometry information. Once we built the document-term matrix containing the words count of the reviews for each business (the reviews are aggregated over each restaurant), we could simply use a matrix factorisation on the counts . To be able to interpret the latent features as topics, we could use a Non-negative matrix factorization (the possible negative features in the SVD cannot stand for cluster assignement). A finer result can be reached with the use of a generative probabilistic model, that's why we chosed the latent dirichlet allocation. The LDA uses a Dirichlet prior on the words distribution over the topics and on the topics distribution over the document which will gives them more freedom than the deterministic approach of the NMF.\\

\section{Latent Dirichlet Allocation}

\subsection*{Model}

The LDA is a three-level hierarchical Bayesian model. The basic idea that documents are represented as random mixtures over latent topics and each topic is characterized by a distribution over words.\\

GRAPHICAL MODEL\\

The generation process for a document \textbf{w} in a corpus D is the following:
\begin{enumerate}
	\item Choose the topics representation $\phi \sim$ Dir($\beta$)
	\item Choose the number of words: $ N \sim $ Poisson($ \xi $)
	\item Choose the distribution of topics $\theta_w \sim$ Dir($\alpha_w$)
	\item For each of the N words:
	\begin{enumerate}
		\item Choose a topic assignement $z_{n,w} \sim$ Multinomial($\theta_w$)
		\item Choose a word $w_n \sim$ Multinomial($\phi_{z_{n,w}}$)
	\end{enumerate}
\end{enumerate}

\subsection*{Parameter Estimation}

The main issue relies in computing the posterior distribution of the hidden variables given a document: 
\begin{align*}
p(\theta, \mathbf{z} |\mathbf{w}, \alpha, \beta) = \frac{p(\theta, \mathbf{z}, \mathbf{w} | \alpha, \beta)}{p(\mathbf{w} | \alpha, \beta)}
\end{align*}

This distribution is intractable. There are two main methods to infer it: through a Gibbs sampler or variational inference. In the first case, we are estimating the hyper parameters $\theta$ and $\phi$ with sample on the different variables. The sampling method will converge to the right model is we sample enough but it takes a lot of time. As a result, we chose the variational inference method which find the variational parameters that optimize a lower bound on the log likelihood. To optimize the bound, we use an expectation maximization method where we estimate the topic distribution for the current document based on its word counts in the E-step and then update the topics distribution in the M-step. \\

Moreover, to increase the speed of our algorithm based on the idea that we have enough reviews, we chose the online variational inference method. This enables to go over each data point only once. For comparison, on the reviews from the Las Vegas data set, a gibbs sampler provided by python executed in around 50 minutes whereas our online method executed in less than 1 minute for equivalent topics evaluation.

\subsection*{Evaluation Method}

We need a measure to evaluate the performance of our model and to tune the hyperparameters. We use perplexity on held-out data as a measure of our model fit. Perplexity is defined as the geometric mean of the log likelihood of the words in the held-out set of docuements given the trained model. In our case, for each document we held out 20\% of the words which constitue the test set.

\begin{align*}
	perplexity(D_{test}) & = \frac{\sum_{d \in D_{test}} log p(words)}{\sum_{d \in D_{test}|d|}}\\
	perplexity(D_{test}) & = \frac{\sum_{d \in D_{test}} \sum_{w \in d} log \left( \sum_{t \in topics} p(w|t) * p(t|d) \right)}{\sum_{d \in D_{test}|d|}}
\end{align*}

We used this measure to optimize the number of topics K and the hyper parameters of the optimization of the lower bound.

\end{document}

### 2015-12-03 latex/poster_parts.tex
poster parts

@@
 
+\subsection*{Next Steps}
+
+So far, we managed to extract the categories of the restaurants as latent features with a latent dirichlet allocation algorithm on the aggregated reviews for each restaurant. \\
+
+A future work could be done on the classification part based on these features: on one hand, clustering the restaurants of different cities and comparing the groups with the existing labels to find new categories or to refine the existing one; on the other hand, we could use the features with classifier to predict the existing categories.
+\\
+
+As a variant, we could try a supervised LDA, where we use the existing categories as a response variable associated with each document and infer the joint model of the documents and the responses.
+Lastly, this method is applicable on each review separately to predict the rating of the review, with a supervised lda also to avoid the predominance of the categories in the topics.
+
 \end{document}

### 2015-12-03 conference_poster_1/main.tex
corrected typos on poster

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Jacobs Landscape Poster
% LaTeX Template
% Version 1.1 (14/06/14)
%
% Created by:
% Computational Physics and Biophysics Group, Jacobs University
% https://teamwork.jacobs-university.de:8443/confluence/display/CoPandBiG/LaTeX+Poster
% 
% Further modified by:
% Nathaniel Johnston (nathaniel@njohnston.ca)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[final]{beamer}

\usepackage[scale=1.24]{beamerposter} % Use the beamerposter package for laying out the poster

\usetheme{confposter} % Use the confposter theme supplied with this template

\setbeamercolor{block title}{fg=ngreen,bg=white} % Colors of the block titles
\setbeamercolor{block body}{fg=black,bg=white} % Colors of the body of blocks
\setbeamercolor{block alerted title}{fg=white,bg=dblue!70} % Colors of the highlighted block titles
\setbeamercolor{block alerted body}{fg=black,bg=dblue!10} % Colors of the body of highlighted blocks
% Many more colors are available for use in beamerthemeconfposter.sty

%-----------------------------------------------------------
% Define the column widths and overall poster size
% To set effective sepwid, onecolwid and twocolwid values, first choose how many columns you want and how much separation you want between columns
% In this template, the separation width chosen is 0.024 of the paper width and a 4-column layout
% onecolwid should therefore be (1-(# of columns+1)*sepwid)/# of columns e.g. (1-(4+1)*0.024)/4 = 0.22
% Set twocolwid to be (2*onecolwid)+sepwid = 0.464
% Set threecolwid to be (3*onecolwid)+2*sepwid = 0.708

\newlength{\sepwid}
\newlength{\onecolwid}
\newlength{\twocolwid}
\newlength{\threecolwid}
\setlength{\paperwidth}{48in} % A0 width: 46.8in
\setlength{\paperheight}{36in} % A0 height: 33.1in
\setlength{\sepwid}{0.024\paperwidth} % Separation width (white space) between columns
\setlength{\onecolwid}{0.22\paperwidth} % Width of one column
\setlength{\twocolwid}{0.464\paperwidth} % Width of two columns
\setlength{\threecolwid}{0.708\paperwidth} % Width of three columns
\setlength{\topmargin}{-0.5in} % Reduce the top margin size
%-----------------------------------------------------------

\usepackage{graphicx}  % Required for including images

\usepackage{booktabs} % Top and bottom rules for tables

%----------------------------------------------------------------------------------------
%	TITLE SECTION 
%----------------------------------------------------------------------------------------

\title{Classification for the Yelp Data Set Challenge} % Poster title

\author{Nicolas Drizard \& Virgile Audi} % Author(s)

\institute{CS281 Final Project, Harvard University} % Institution(s)

%----------------------------------------------------------------------------------------

\begin{document}

\addtobeamertemplate{block end}{}{\vspace*{2ex}} % White space under blocks
\addtobeamertemplate{block alerted end}{}{\vspace*{2ex}} % White space under highlighted (alert) blocks

\setlength{\belowcaptionskip}{2ex} % White space under figures
\setlength\belowdisplayshortskip{2ex} % White space under equations

\begin{frame}[t] % The whole poster is enclosed in one beamer frame

\begin{columns}[t] % The whole poster consists of three major columns, the second of which is split into two columns twice - the [t] option aligns each column's content to the top

\begin{column}{\sepwid}\end{column} % Empty spacer column

\begin{column}{\onecolwid}\vspace{-0.6in} % The first column

%----------------------------------------------------------------------------------------
%	OBJECTIVES
%----------------------------------------------------------------------------------------

\begin{alertblock}{Objectives}
\small
We are taking part in the Yelp Dataset challenge round 6. We chosed to solve the question of infering categories based on the reviews. The goal is to build a finer way to categorize the Yelp businesses.\\

Our approach consists in using Latent Dirichlet Allocation to build latent features from the text reviews which would depict the categories of each business and turn it into a vector representation which carries local geometry information. We then resorted to building a network of restaurant based on this underlying geometry and cluster this network using a graph theory algorithm.\\

\end{alertblock}

%----------------------------------------------------------------------------------------
%	INTRODUCTION
%----------------------------------------------------------------------------------------

\begin{block}{The Data}
\small
\begin{itemize}
		\item 1.6 million reviews
		\item 61 000 businesses
		\item 481 000 attributes (ie hours, parking availabity, take-out, ambience)
		\item aggregated check-in measurements over time
\end{itemize}

We cleaned and prepared restaurants data in the city of Las Vegas, NV to grasp in a finer manner the local relationships of the restaurants. This also makes more sense on from the user's perspective.\\

\end{block}

\begin{block}{Latent Dirichlet Allocation}
\small

LDA \cite{LDA} is a three-level hierarchical Bayesian model. Documents are represented as random mixtures over latent topics and each topic is characterized by a distribution over words. \\
The generative process for a document \textbf{w} in a corpus D is the following:
\begin{enumerate}
	\item Choose the topics representation $\phi \sim$ Dir($\beta$)
	\item Choose the number of words: $ N \sim $ Poisson($ \xi $)
	\item Choose the distribution of topics $\theta_w \sim$ Dir($\alpha_w$)
	\item For each of the N words:
	\begin{enumerate}
		\item Choose a topic assignement $z_{n,w} \sim$ Multinomial($\theta_w$)
		\item Choose a word $w_n \sim$ Multinomial($\phi_{z_{n,w}}$)
	\end{enumerate}
\end{enumerate}
We chose an online variational inference algorithm \cite{OLLD} which showed significant speed improvement when compared to the LDA python package using Gibbs sampling. To fit an LDA model with 50 topics on a 4000 document corpus and 10000 words took:
$$ \text{Online} = 1m13s \quad \text{Gibbs} = 50m $$
\end{block}
%------------------------------------------------

\begin{figure}
\includegraphics[width=0.5\linewidth]{LDA.png}
\caption{Graphical Model Representation of LDA}
\end{figure}

%----------------------------------------------------------------------------------------

\end{column} % End of the first column

\begin{column}{\sepwid}\end{column} % Empty spacer column

\begin{column}{\twocolwid} % Begin a column which is two columns wide (column 2)
\begin{figure}
\includegraphics[width=0.6\linewidth]{posterpicture4.png}
\end{figure}

\begin{column}{\twocolwid} % The first column within column 2 (column 2.1)
\begin{figure}
\includegraphics[width=1\linewidth]{dendo_3-1.png}
\caption{Overall Process}
\end{figure}

\end{column}

\begin{columns}[t,totalwidth=\twocolwid]\hspace{-0.6in} % Split up the two columns wide column again

\begin{column}{\onecolwid} % The first column within column 2 (column 2.1)

%----------------------------------------------------------------------------------------
%	MATHEMATICAL SECTION
%----------------------------------------------------------------------------------------

\begin{block}{Evaluation}
\small
Perplexity is defined as the geometric mean of the log likelihood of the words in the held-out set of docuements given the trained model. In our case, for each document we held out 20\% of the words which constitue the test set.
\end{block}

%----------------------------------------------------------------------------------------

\end{column} % End of column 2.1

\begin{column}{\onecolwid}\hspace{-0.6in} % The second column within column 2 (column 2.2)

%----------------------------------------------------------------------------------------
%	RESULTS
%----------------------------------------------------------------------------------------
\small
\vfill{The formula is given by:}
\begin{center}
$$
	\boxed{\quad\text{perp}(D_{test}) = \frac{\sum_{d \in D_{test}} \sum_{w \in d} \log \left( \sum_{t \in topics} p(w|t) p(t|d) \right)}{\sum_{d \in D_{test}|d|}}\quad}
$$

\end{center}
%----------------------------------------------------------------------------------------

\end{column} % End of column 2.2

\end{columns} % End of the split of column 2

%----------------------------------------------------------------------------------------

\end{column} % End of the second column

\begin{column}{\sepwid}\end{column} % Empty spacer column

\begin{column}{\onecolwid}\vspace{-0.6in} % The third column

%----------------------------------------------------------------------------------------
%	CONCLUSION
%-----------------------------------------------------------
\begin{block}{Graph Theory}
\small
 The intuition behind the Walktrap algorithm is that random walks on a graph tend to get "trapped into densely connected parts corresponding to communities".\cite{Gr} It is a clustering algorithm based on the definition of a new metric to evaluate the distance between two vertices in a graph:
 $$r_{ij} = \sqrt{\sum\limits_{k=1}^{n}\frac{(P^t_{ik}-P^t_{kj})^2}{d(k)}}$$
 where $P^t_{ik}$ is the transition probability at time t and $d(k)$ is the degree of node k (number of edges incident to the vertex)
\end{block}

%----------------------------------------------------------------------------------------
%	ADDITIONAL INFORMATION
%----------------------------------------------------------------------------------------

\begin{block}{Results}\vspace{-0.2in}
\small
\begin{itemize}
\item The validation indicate that \textbf{50} was the optimum number of topics, some of these topics are plotted in the diagram 
\item Based on the Shannon distance (symmetric KL divergence) between two documents, we set a threshold of 1 and created the adjacency matrix
\item In order to inspect the graph and due to its extremely large size ($\>2 10^{6}$ edges), we sampled 500 restaurants having among their tags either "Chinese", "Seafood" or "Mexican"
\item We ran the walktrap clustering algorithm in R. It initialy found 7 cliques, but a closer inspection of the dendogram, we actually noticed that it subcategories 3 bigger cliques boxed in green, red, and blue, which corresponded almost exactly to the 3 classes of restaurants !
\end{itemize}

\end{block}
\begin{alertblock}{Conclusion}
\small
By using a combination of unsupervised learning and graph theory, we managed to retrieve most of the original classification that is up to now still done by hand ! This work could result in an automation tool for Yelp to label properly its database. 
\end{alertblock}

\begin{block}{Next steps}\vspace{-0.2in}
\small
Futur work could focus on the sub-cliques and try to get a finer classification by combining them with other features like check-ins, parking availability, etc. As a variant, we could also try a supervised LDA, where we use the existing categories as a response variable associated with each document and infer the joint model of the documents and the responses.
\end{block}

%----------------------------------------------------------------------------------------
%	REFERENCES
%----------------------------------------------------------------------------------------

\begin{block}{References}
\nocite{*} % Insert publications even if they are not cited in the poster
\tiny{\bibliographystyle{unsrt}
\bibliography{sample}}

\end{block}

\end{column} % End of the third column

\end{columns} % End of all the columns in the poster

\end{frame} % End of the enclosing frame

\end{document}

### 2015-12-07 conference_poster_1/main.tex

@@
 \begin{figure}
-\includegraphics[width=0.6\linewidth]{posterpicture4.png}
+\includegraphics[width=0.6\linewidth]{posterpicture3.jpg}
 \end{figure}
@@
 \item We ran the walktrap clustering algorithm in R.
-It initialy found 7 cliques, but a closer inspection of the dendogram, we actually noticed that it subcategories 3 bigger cliques boxed in green, red, and blue, which corresponded almost exactly to the 3 classes of restaurants !
+It initialy found 7 cliques, but a closer insepction of the dendogram, we actually noticed that it subcategories 3 bigger cliques boxed in green, red, and blue, which corresponded almost exactly to the 3 classes of restaurants !
 \end{itemize}
@@
 \small
-By using a combination of unsupervised learning and graph theory, we managed to retrieve most of the original classification that is up to now still done by hand !
-This work could result in an automation tool for Yelp to label properly its database.
+By using a combination of unsupervised learning and graph theory, we managed to retrieve most of the original classification that is up to now still done at hand !
+This work could result in an au tomation tool for Yelp to label properly its data based.
 \end{alertblock}
@@
 \small
-Futur work could focus on the sub-cliques and try to get a finer classification by combining them with other features like check-ins, parking availability, etc.
+Futur work could focus on the sub-cliques and try to get a more refine classification by combining them with other features like check-ins, parking availability, etc.
 As a variant, we could also try a supervised LDA, where we use the existing categories as a response variable associated with each document and infer the joint model of the documents and the responses.

### 2015-12-08 latex/poster_parts.tex
supervised learning

@@
 
+\section{Classification}
+
+Once the feature has been extracted, we can apply supervised learning methods to classify the Yelp restaurants based on their labels on Yelp.
+Several approaches are possible with regards to the features to solve this multi-labels classigication task
+
+\subsection*{Features}
+
+The features are divided into two main parts: on one hand, the topics assignements extracted from the reviews with the LDA and on the other hand, the properties provided by Yelp.
+Pre-processing the latter part provided a 198 dimensionnal vector.
+These features contain both numerical features (rating, space coordinates, number of reviews, customer check-in...) and categorical features converted into indicator variables.
+
+\subsection*{Methods}
+
+The outputs of our classification are the labels of each restaurant.
+We chose to train several binary classifiers to predict one label at a time with a One-Vs-All approach.
+The high dimensionnality of the features and the large number of indicator varibales induces a high sparsity.
+As a result, a sufficiently robust algorithm need to be used.
+One particularity is also that the classes are all really skewed, the dummy baseline where we do not predict  any label for all the restaurant has a really high score.\\
+
+\begin{center}
+    \begin{tabular}{| l | l | l | l |}
+    \hline
+    & OVI LDA & GS LDA & NMF \\ \hline
+    All False & 90,02 \% &  90.02 \% &  90.02 \% \\ \hline
+    kernel rbf SVM & 90,81\% &  90.38\% &  90.38\% \\ \hline
+    kernel rbf SVM + PCA & 90.83\% &  90.60\% &  90.57\% \\ \hline
+    Logistic Regression & 90.84\% &  91.89\%  &  91.24\%\\ \hline
+    Logistic Regression + PCA & 92.59\% &  92.53\% &  92.68\% \\ \hline
+    Lasso & 90.82\% &  93.44\% &  92.01\% \\ \hline
+	Lasso + PCA & 93.44\%  &  \textbf{94.46} \%  &  93.08\% \\ \hline
+    Random Forest & 91.90\% &  93.31\% &  92.89\% \\ \hline
+    Random Forest + PCA & 93.63\% &  94.04\% &  93.44\% \\ \hline
+    \end{tabular}
+\end{center}
+
+We first coded a l2 regularized logistic regression and use scikit learn for the other methods.
+The random forest provides the best predictor expected as it corresponds to an ensemble method that combines multiple decision trees, leading to a more robust model.
+We showed the ROC curves that we obtained.
+The variance of the classifiers with regards to the class used as output is quite high.
+This could be explained by the relative skewness of each class and also their own specificity.
+Moreover, using dimensionality reduction method on the Yelp check-ins information before the classificationthe PCA also improved the accuracy.
+These features contains the average number of customers for each hour of the week which leads to a vector of dimension 168.
+The principal component analysis dropped it down to 13, while keeping 94\% of the variance.
+
+\begin{figure}[H]
+	\includegraphics[scale=0.55]{img/roc_lasso.png}
+	\centering
+\end{figure}
+
+\begin{figure}[H]
+	\includegraphics[scale=0.55]{img/roc_rf.png}
+	\centering
+\end{figure}
+
+Moreover, this method provides a way to sort the features by importance.\\
+
+FEATURES IMPORTANCE
+
 \end{document}

### 2015-12-08 OVI/lda_ovi.py

@@ -1,0 +1,151 @@
+import lda_vi_cython
+import numpy as np
+import threading
+
+
+class LDA:
+
+    def __init__(self, num_topics, num_threads=1):
+        self.num_topics = num_topics
+        self.num_threads = num_threads
+        self.topics = None
+        self.gamma = None
+
+    def set_topics(self, n):
+        self.num_topics = n
+
+    def set_threads(self, t):
+        self.num_threads = t
+
+    def fit(self, dtm, batch_size, tau=512, kappa=0.7):
+        '''
+        Parallel version of the lda: the temporary topics are computed in
+        parallel for each document inside a mini-batch
+
+        '''
+        # Initialisation
+        num_docs, num_words = dtm.shape
+        np.random.seed(0)
+        topics = np.random.gamma(100., 1./100., (self.num_topics, num_words))
+        gamma = np.ones((num_docs, self.num_topics))
+        ExpELogBeta = np.zeros((self.num_topics, num_words))
+        topics_int = np.zeros((self.num_threads, self.num_topics, num_words))
+
+        num_batch = num_docs / batch_size
+        batches = np.array_split(
+            np.arange(num_docs, dtype=np.int32), num_batch)
+
+        for it_batch in range(num_batch):
+            lda_vi_cython.exp_digamma_arr(topics, ExpELogBeta)
+
+            docs_thread = np.array_split(batches[it_batch], self.num_threads)
+
+            # vector of threads
+            threads = [None]*self.num_threads
+
+            for tid in range(self.num_threads):
+                threads[tid] = threading.Thread(target=self.worker_estep,
+                                                args=(docs_thread[tid], dtm,
+                                                      topics_int[tid, :, :],
+                                                      gamma, ExpELogBeta))
+                threads[tid].start()
+
+            for thread in threads:
+                thread.join()
+
+            # Synchronizing the topics_int
+            topics_int_tot = np.sum(topics_int, axis=0)
+            # Initialize the list of topics int for the next batch
+            topics_int[:, :, :] = 0
+            # M-step
+            indices = (np.sum(dtm[batches[it_batch], :], axis=0) > 0).astype(
+                np.int32)
+            lda_vi_cython.m_step(topics, topics_int_tot, indices, num_docs,
+                                 batch_size, tau, kappa, it_batch)
+
+        self.topics = topics
+        self.gamma = gamma
+
[…]

### 2015-12-09 paper/article_2.tex
Latex article

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Journal Article
% LaTeX Template
% Version 1.3 (9/9/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Frits Wenneker (http://www.howtotex.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[twoside]{article}

\usepackage{lipsum} % Package to generate dummy text throughout this template

\usepackage[sc]{mathpazo} % Use the Palatino font
\usepackage[T1]{fontenc} % Use 8-bit encoding that has 256 glyphs
\linespread{1.05} % Line spacing - Palatino needs more space between lines
\usepackage{microtype} % Slightly tweak font spacing for aesthetics
\usepackage{paralist}
\usepackage[margin={1.5cm,1.5cm},top=32mm,columnsep=20pt]{geometry} % Document margins
\usepackage{multicol} % Used for the two-column layout of the document
\usepackage[hang, small,labelfont=bf,up,textfont=it,up]{caption} % Custom captions under/above floats in tables or figures
\usepackage{booktabs} % Horizontal rules in tables
\usepackage{graphicx,float}
\usepackage{float} % Required for tables and figures in the multi-column environment - they need to be placed in specific locations with the [H] (e.g. \begin{table}[H])
\usepackage{hyperref} % For hyperlinks in the PDF
\usepackage{amsmath,amsfonts,amsthm}
\usepackage{lettrine} % The lettrine is the first enlarged letter at the beginning of the text
\usepackage{paralist} % Used for the compactitem environment which makes bullet points with less space between them

\usepackage{abstract} % Allows abstract customization
\renewcommand{\abstractnamefont}{\normalfont\bfseries} % Set the "Abstract" text to bold
\renewcommand{\abstracttextfont}{\normalfont\small\itshape} % Set the abstract itself to small italic text

\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
\makeatletter
\def\BState{\State\hskip-\ALG@thistlm}
\makeatother

\usepackage{titlesec} % Allows customization of titles
\renewcommand\thesection{\arabic{section}} % Roman numerals for the sections
\renewcommand\thesubsection{\arabic{subsection}} % Roman numerals for subsections
\titleformat{\section}[block]{\Large\scshape\centering}{\thesection.}{1em}{} % Change the look of the section titles
\titleformat{\subsection}[block]{\large}{\thesection.\thesubsection.}{1em}{} % Change the look of the section titles

\usepackage{fancyhdr} % Headers and footers
\pagestyle{fancy} % All pages have headers and footers
\fancyhead{} % Blank out the default header
\fancyfoot{} % Blank out the default footer
\fancyhead[C]{Userless Classificaton for the Yelp Dataset Challenge} % Custom header text
\fancyfoot[RO,LE]{\thepage} % Custom footer text

%----------------------------------------------------------------------------------------
%	TITLE SECTION
%----------------------------------------------------------------------------------------

\title{\vspace{-15mm}\fontsize{24pt}{10pt}\selectfont\textbf{Userless Classificaton for the Yelp Dataset Challenge}} % Article title

\author{
\large
\textsc{Nicolas Drizard \& Virgile Audi}\\[2mm] % Your name
\normalsize Final Project for CS281, Harvard University \\ % Your institution
\normalsize {nicolas.drizard@g.harvard.edu \quad vaudi@g.harvard.edu} % Your email address
\vspace{-5mm}
}
\date{}

%----------------------------------------------------------------------------------------

\begin{document}

\maketitle % Insert title

\thispagestyle{fancy} % All pages have headers and footers

%----------------------------------------------------------------------------------------
%	ABSTRACT
%----------------------------------------------------------------------------------------

\begin{abstract}

\noindent

We planned on building latent features from the text reviews which would depict the cat- egories of the business. To put it in a nutshell, we would like to build from the text reviews of an entry a vector representation which carries local geometry information. Once we built the document-term matrix containing the words count of the reviews for each business (the reviews are aggregated over each restaurant), we could simply use a matrix factorisation on the counts . To be able to interpret the latent features as topics, we could use a Non-negative matrix factorization (the possible negative features in the SVD cannot stand for cluster as- signement). A finer result can be reached with the use of a generative probabilistic model, that’s why we chosed the latent dirichlet allocation. The LDA uses a Dirichlet prior on the words distribution over the topics and on the topics distribution over the document which will gives them more freedom than the deterministic approach of the NMF.

\end{abstract}

%----------------------------------------------------------------------------------------
%	ARTICLE CONTENTS
%----------------------------------------------------------------------------------------

\begin{multicols}{2} % Two-column layout throughout the main article text

\section{Introduction}

\lettrine[nindent=0em,lines=1]{T}he classification system in Yelp is manual. When the owner of a business creates a page for his restaurant or bar, he is asked to enter a certain number of attributes or "tags". Yelp users can then alter or even add some new tags based on their experiences. As part of the Yelp Data Set Challenge Round 6, we decided to tackle the issue of classification with ultimate objective to be able to create an automathised method to classify venues, based on the information contained on the business' webage and most importantly the written reviews from Yelpers. This project can be divided in two parts, the first on Feature Extraction and the second on classification and clustering. In more details, we applied various dimensionality reduction methods such as Latent Dirichlet Allocation (LDA) or Non-negative Matrix Factorisation (NMF) to map the reviews into a geometrical space. We then decided to compare both supervised approaches such as Multinomial Regression and unsupervised approaches, for instance the Walktrap algorithm, to the problem of classification on the Yelp dataset.
%------------------------------------------------

\section{Data}

Yelp provides data on all kinds of venues such as dentists or bars in 5 cities in the United-States and Europe. The data can be summarised as follows:

\begin{compactitem}
	\item 1.6 million reviews
	\item 61 000 businesses		
	\item 481 000 attributes 
	\item aggregated check-in measurements over time
\end{compactitem}

\noindent For simplicity, we chose to focus on restaurants and bars in the city of Las Vegas, Nevada. We reduced the data to a dataset of 3822 businesses, about 20 thousands reviews and 250 other features such as hours, parking availabity, take-out, ambience. If the numerical data we received from Yelp was mostly cleaned, it was not the case of the text data. Cleaning the reviews represented a significant part of this final project. We present some of the steps we followed in the process:\\

\begin{compactitem}
	\item We aggregated all the reviews about a particular business into a "super" review, in order to get a general sense of what the restaurant was about,
	\item We applied spelling corrections, removed common stopwords and generic words such as "table" or "restaurants",
	\item We attempted at only selecting common words and not adjectives in order to focus on what the venues were about and not the users' opinions,
	\item We transformed the corpus of "super reviews" into a document-term matrix that we could exploit.
\end{compactitem}

%------------------------------------------------

\section{Feature Extraction}

\subsection{Approach}

To extract content from the reviews, we applied 2  methods from Topic Modeling to reduce the document term matrix into meaningful information. We first looked at LDA, using both a Gibbs sampler and Online Variational Inference (OVI) algorithm. Note that we used the Gibbs sampler as a way to benchmark our coded OVI. The motivation behind OVI is twofold. First, it appeared more appropriate to the data we were working with, indeed new reviews can always be added to the corpus in continuous flow. Second, it showed some extremely significant time improvement over the Gibbs sampler version in Python (cf figure 1). We also wanted to compare the performance of LDA with a non-probabilistic approach which is NMF.

\subsection{Latent Dirichlet Allocation}

The LDA is a three-level hierarchical Bayesian model. The basic idea that documents are represented as random mixtures over latent topics and each topic is characterized by a distribution over words.\\

\noindent The generative process for a document \textbf{w} in a corpus D is the following:
\\
\begin{compactenum}
	\item Choose the topics representation:\newline $\phi \sim$ Dir($\beta$)
	\item Choose the number of words:\newline $ N \sim $ Poisson($ \xi $)
	\item Choose the distribution of topics:\newline $\theta_w \sim$ Dir($\alpha_w$)
	\item For each of the N words:
	\begin{compactenum}
		\item Choose a topic assignement:\newline $z_{n,w} \sim \text{Multinomial}(\theta_w)$
		\item Choose a word: \newline$w_n \sim \text{ Multinomial}(\phi_{z_{n,w}})$
	\end{compactenum}
\end{compactenum}

\begin{figure}[H]
\centering
\includegraphics[width=0.8\linewidth]{LDA.png}
\caption{Graphical Model Representation of LDA}
\end{figure}

\subsection{Parameter Estimation and algorithm:}

The main issue relies in computing the posterior distribution of the hidden variables given a document:\\

\begin{align*}
p(\theta, \mathbf{z} |\mathbf{w}, \alpha, \beta) = \frac{p(\theta, \mathbf{z}, \mathbf{w} | \alpha, \beta)}{p(\mathbf{w} | \alpha, \beta)}
\end{align*}

\noindent This distribution is intractable. As mentioned above, we used two  methods to infer it: through a Gibbs sampler or variational inference. In the first case, we are estimating the hyper parameters $\theta$ and $\phi$ with samples on the different variables. Alternatively, we chose the online variational inference method which finds the variational parameters that optimize a lower bound on the loglikelihood. The setup of the Variational Inference is as follows. We first approximate the true posterior by a simpler and factorised distribution:
$$q(\boldsymbol{z},\boldsymbol{\theta},\boldsymbol{\beta}) = q(\boldsymbol{z})q(\boldsymbol{\theta})q(\boldsymbol{\beta}) $$

\noindent where:
$$ q(z_{di} = k) = \phi_{d_{w_{di}k}} \quad q(\theta_d) = \text{Dir}(\theta_d,\gamma_d) \quad q(\beta_k) = \text{Dir}(\beta_k,\lambda_k) $$

\noindent The $\boldsymbol{\gamma}$ parameter rule the topic assignments for each document and the $\boldsymbol{\lambda}$, the topics themselves. We then minimise the KL divergence between the distribution $q$ and the true posterior $p$ like for the usual variational inference. What differs in online variational inference is that we sample a batch of document at each step and perform the E-step as if this batch constituted the entire corpus. We present the algorithm below:

\begin{algorithm}[H]
\caption{Batched Online Variational Inference}\label{euclid}
\begin{algorithmic}[1]
\State Define $\rho_t \equiv (\tau_0 + t)^{-\kappa}$
\State Initalise $\boldsymbol{\lambda}$ randomly
\State Sample a batch $\mathcal{S}$ of documents of size S
\For {$d$ in $\mathcal{S}$}
\While {$\gamma_(d)$ hasn't converged}
\State Set $\phi^{(d)}_{twk} \propto \exp\{\mathbb{E}_q\log\theta_{tk} + \mathbb{E}_q\log\beta_{kw}\}$
\State Set $\gamma^{(d)}_{tk} = \alpha + \sum_{w} \phi^{(d)}_{twk}n_{tw}$
\EndWhile
\State Compute $\tilde{\lambda}_{kw} = \eta +\frac{D}{S}n_{tw}\phi^{(d)}_{twk}$
\EndFor
\State $\boldsymbol{\lambda} = (1-\rho_t)\boldsymbol{\lambda}+\rho_t\boldsymbol{\tilde{\lambda}}$
\State $t = t+1$
\State \textbf{goto} 3 and repeat until all documents are observed.
\end{algorithmic}
\end{algorithm}

\noindent where $\kappa \in (0.5,1]$ rules how fast we forget old values of $\tilde{\lambda}$ and $\tau_{0}$ how much weight one wants to put on the first iterations.

\subsection{Evaluation Method}

We need a measure to evaluate the performance of our model and to tune the hyperparameters. We use perplexity on held-out data as a measure of our model fit. Perplexity is defined as the geometric mean of the log likelihood of the words in the held-out set of docuements given the trained model. In our case, for each document we held out 20\% of the words which constitue the test set.

\begin{align*}
	perplexity(D_{test}) & = \frac{\sum\limits_{d \in D_{test}} \log p(words)}{\sum\limits_{d \in D_{test}|d|}}\\
	perplexity(D_{test}) & = \frac{\sum\limits_{d \in D_{test}} \sum\limits_{w \in d} \log \left( \sum_{t \in topics} p(w|t)p(t|d) \right)}{\sum\limits_{d \in D_{test}|d|}}
\end{align*}

\noindent We used this measure to optimize the number of topics K and the hyper parameters of the optimization. We also used the perplexity to benchmark our algorithm with the Gibbs sampler in the LDA 1.0.3 package in Python:

$$\text{perp}_{OVI} = XX \quad \text{and} \quad \text{perp}_{GS} = XX$$

\subsection{Results}
Another way to assess the performance of our LDA was to inspect the topics outputted by the algorithm. We present some of the most significant topics:\\

\begin{figure}[H]
\centering
\includegraphics[width=1\linewidth]{topics.png}
\caption{Topics extracted from the Las Vegas reviews using OVI}
\end{figure}

\noindent We obtained similar results using the NMF approach. The topics themselves were not our primary interested. As mentioned in the introduction, we were using these methods primarly for dimensional reduction purposes. We now present two different approaches to answer the question of classification using supervised and unsupervised machine learning.\\

%------------------------------------------------
\section{Supervised Classification}

\section{Unsupervised Clustering}
\subsection{Approach}

For this part of the project, we use the same features as for the supervised classification approach, i.e. the topic assignments. We wanted to see if it was possible to retrieve the original classification only based on the reviews. To do so and in order to check if our classification attempt was successful, we sampled about 1000 restaurants having tags in the following list of 6 categories: Sushi, Steakhouse, Seafood, Mexican, Sports and Breakfast \& Brunch. We then applied applied the following methodology.\\

Each restaurant is now represented as probability distribution over the latent topics. Using the Shannon distance (symmetric Kullback-Liebler Divergence), we created a distance matrix gathering information on how close 2 restaurants are based on their reviews. After many experimentations, we chose to transform this distance matrix into a weighted adjacency matrix:\\

\begin{compactitem}
\item $w_{ij} = 5$ if $d_{Shannon}(r_i,r_j)<1$,
\item $w_{ij} = 0.1$ otherwise.\\
\end{compactitem}

\noindent The choice of having a non-zero weight between two restaurants even though they are not "close" is motivated by the fact that many graph clustering algorithm and in particular the WalkTrap algorithm that we used and present next, will only work on a connected graph.\\

\noindent We then transformed this adjacency matrix in an unweighted graph and applied the Walktrap algorithm for community detection.\\

\subsection{The WalkTrap Algorithm}
The WalkTrap Algorithm is a community detection algorithm created by Pascal Pons and Matthieu Latapy. The algortihm runs in time $O(n^2\log n)$ and space $O(n^2)$ where $n$ is the number of vertices in the graph. As mentioned in their paper, "the intuition behind the Walktrap is that random walks on a graph tend to get trapped into densely connected parts corresponding to communities".\cite{Gr} It relies on a new metric used to evaluate the distance between two vertices in a graph:
 $$r_{ij} = \sqrt{\sum\limits_{k=1}^{n}\frac{(P^t_{ik}-P^t_{kj})^2}{d(k)}}$$
 where $P^t_{ik}$ is the transition probability in $t$ steps and $d(k)$ is the degree of node k (number of edges incident to the vertex). We can then generalise this distance between two vertices to a distance between two communities. Using this distance, we can now apply a hierarchical clustering algorithm.

\begin{algorithm}[H]
\caption{Walktrap Algorithm}\label{euclid}
\begin{algorithmic}[1]
\State Start with a partition $\mathcal{P}_1=\{\{v\}, v \in V\}$
\State Compute the distances between all adjacent vertices
\While {$\mathcal{P}_t\neq V$}
\State Merge 2 communities $\mathcal{C}_i$ and $\mathcal{C}_j$ in $\mathcal{P}_k$ and create a new partition $\mathcal{P}_{k+1}$
\State Evaluate the distances between the communities in this new partition
\EndWhile
\end{algorithmic}
\end{algorithm}

\noindent The choice of communities to merge in step 4 is made using Ward's method. We look at minimising the mean within-cluster variance:
$$\frac{1}{n_\mathcal{C}}\sum\limits_{\mathcal{C}\in\mathcal{P}_{k}}\sum\limits_{i\in\mathcal{C}}r^2_{i\mathcal{C}},$$
\noindent where $n_\mathcal{C}$ is the number of communities at iteration $k$, and $r_{i\mathcal{C}}$ is the distance from vertex i to its community $\mathcal{C}$.\\

\subsection{Results}

Running the algorithm from the \emph{igraph} in R, we outputted a dendogram (cf. Figure 3) representing the obtained clustering. We colored the tag of each business for a better readability.  It is not yet entirely clear to us how to get the optimum number of clusters. We were puzzled to see that the Walktrap algorithm indicated that a cut into 3 big clusters represented the optimum partition. Knowing the structure of the sampled restaurants, we decided to further investigate the dendogram. As one can see on Figure 3, cutting the tree at different heights, we can obtain 5 clear colored communities, corresponding to 5 of the 6 tags we pre-selected.\\

\noindent We summarized this classification using a confusion matrix: 
\begin{figure}[H]
\centering
\includegraphics[width=1\linewidth]{confusion}
\caption{Confusion Matrix using the Walktrap Algorithm}
\end{figure}

\noindent With this method, we managed to detect 4 communities with great accuracy (over 80\%). Nevertheless, this classification still has some flaws and the most obvious one is the misclassification or even non-classification of the Sports bars (yellow). We focused a bit more on these venues and explored manually the tags associated with them. We noticed that these Sports bar were most of the time having other tags such as "Restaurants","Bar", "American" and some even "Mexican". Reviews for these venues might have been misallocated due to the proximity of types of food, drinks or "ambiance" with Mexican restaurants. It is nonetheless interesting to note that were grouped almost all together inside the Mexican restaurants, and that if we cut the three at the sixth level then they would all be gathered in 2 cliques.\\

\noindent It seems that this method will succeed in making a difference between communities of restaurants if they are almost exlusive. It seems very unlikely to discover a restaurant that one can identify as both a Mexican and a Sushi place or even a Sushi place specialising in Breakfast (unless its speciality is the takagoyaki, a type of Japanese omelette made by "rolling together several layers of cooked egg"). It was often the case that misclassified restaurant had the tag "Buffet" which is for our purpose of classification our worst ennemy as it will phagocytose many categories at once.

\begin{figure*}
\centering
\includegraphics[angle=90,width=0.25\linewidth]{den_ovi2-1.png}
\caption{Dendogram outputted by the Walktrap Algorithm}
\end{figure*}
\newpage

\section{Next steps}
Futur work could focus on the sub-cliques and try to get a finer classification by combining them with other features like check-ins, parking availability, etc. As a variant, we could also try a supervised LDA, where we use the existing categories as a response variable associated with each document and infer the joint model of the documents and the responses.

\section{conclusion}
By using a combination of unsupervised learning and graph theory, we managed to retrieve most of the original classification that is up to now still done by hand ! This work could result in an automation tool for Yelp to label properly its database.

%----------------------------------------------------------------------------------------
%	REFERENCE LIST
%----------------------------------------------------------------------------------------

\nocite{*} % Insert publications even if they are not cited in the poster
\bibliographystyle{unsrt}
\bibliography{sample}
\end{multicols}

\end{document}

%----------------------------------------------------------------------------------------

### 2015-12-09 OVI/lda_ovi.py
tests

@@ -111,7 +111,7 @@ class LDA:
         '''
         gamma = self.transform(dtm_test, tau, kappa)
         # Normalizing the topics and gamma
-        topics = self.topics/self.topics.sum(axis=0)
+        topics = self.topics/self.topics.sum(axis=1)[:, np.newaxis]
         gamma = gamma/gamma.sum(axis=1)[:, np.newaxis]
 
         if len(gamma.shape) == 1:

### 2015-12-10 paper/article_2.tex

@@
 The LDA is a three-level hierarchical Bayesian model.
-The basic idea that documents are represented as random mixtures over latent topics and each topic is characterized by a distribution over words.\\
+The basic idea that documents are represented as random mixtures over latent topics and each topic is characterized by a distribution over words.\cite{LDA}\\
 
@@
 Alternatively, we chose the online variational inference method which finds the variational parameters that optimize a lower bound on the loglikelihood.
-The setup of the Variational Inference is as follows.
+The setup \cite{OLLD} of the Variational Inference is as follows.
 We first approximate the true posterior by a simpler and factorised distribution:
@@
 \subsection{The WalkTrap Algorithm}
-The WalkTrap Algorithm is a community detection algorithm created by Pascal Pons and Matthieu Latapy.
+The WalkTrap Algorithm is a community detection algorithm created by Pascal Pons and Matthieu Latapy \cite{Gr}.
 The algortihm runs in time $O(n^2\log n)$ and space $O(n^2)$ where $n$ is the number of vertices in the graph.

### 2015-12-10 paper/article_2.tex
Work on paper

@@
 \begin{align*}
-	perplexity(D_{test}) & = \frac{\sum\limits_{d \in D_{test}} \log p(words)}{\sum\limits_{d \in D_{test}|d|}}\\
-	perplexity(D_{test}) & = \frac{\sum\limits_{d \in D_{test}} \sum\limits_{w \in d} \log \left( \sum_{t \in topics} p(w|t)p(t|d) \right)}{\sum\limits_{d \in D_{test}|d|}}
+	perplexity(D_{test}) & = \frac{\sum\limits_{d \in D_{test}} \log p(words)}{\sum\limits_{d \in D_{test}}|d|}\\
+	perplexity(D_{test}) & = \frac{\sum\limits_{d \in D_{test}} \sum\limits_{w \in d} \log \left( \sum_{t \in topics} p(w|t)p(t|d) \right)}{\sum\limits_{d \in D_{test}}|d|}
 \end{align*}
@@
 \noindent We used this measure to optimize the number of topics K and the hyper parameters of the optimization.
-We also used the perplexity to benchmark our algorithm with the Gibbs sampler in the LDA 1.0.3 package in Python:
+We also used the perplexity on the training set to benchmark our algorithm with the Gibbs sampler in the LDA 1.0.3 package in Python:
 
-$$\text{perp}_{OVI} = XX \quad \text{and} \quad \text{perp}_{GS} = XX$$
+$$\text{perp}_{OVI} = -6.78 \quad \text{and} \quad \text{perp}_{GS} = -6.45$$
+
+\begin{figure}[H]
+\centering
+\includegraphics[width=1\linewidth]{V.png}
+\caption{Cross Validation over the number of Topics}
+\end{figure}
 
@@
 As mentioned in the introduction, we were using these methods primarly for dimensional reduction purposes.
+\\
+
+We would like to also make a general comment about the Online Variational algorithm.
+We noticed that the OVI algorithm is extremely sensitive to the hyperparametrisation, i.e the batch size $S$, the forgetfullness parameter $\kappa$ and the early iterations weith parameter $\tau$.
+This was also noted by Tamara Broderick, Nicholas Boyd, Andre Wibisono and Ashia C.
+Wilson in their paper\cite{svi}.
+In addition to validating the number of topics, validating over these parameters was crucial to obtain valuable resutls.\\
+
 We now present two different approaches to answer the question of classification using supervised and unsupervised machine learning.\\
@@
 \end{figure*}
-\newpage
 

### 2015-12-11 paper/article_2.tex

@@
 \usepackage{paralist} % Used for the compactitem environment which makes bullet points with less space between them
+\usepackage{subfigure}% For side by side figure
 
@@
 Yelp users can then alter or even add some new tags based on their experiences.
-As part of the Yelp Data Set Challenge Round 6, we decided to tackle the issue of classification with ultimate objective to be able to create an automathised method to classify venues, based on the information contained on the business' webage and most importantly the written reviews from Yelpers.
-This project can be divided in two parts, the first on Feature Extraction and the second on classification and clustering.
-In more details, we applied various dimensionality reduction methods such as Latent Dirichlet Allocation (LDA) or Non-negative Matrix Factorisation (NMF) to map the reviews into a geometrical space.
-We then decided to compare both supervised approaches such as Multinomial Regression and unsupervised approaches, for instance the Walktrap algorithm, to the problem of classification on the Yelp dataset.
+As part of the Yelp Data Set Challenge Round 6, we decided to tackle the issue of classification with ultimate objective to be able to create an automatised method to classify venues, based on the information contained on the business' web page and most importantly the written reviews from Yelpers.
+\\
+
+This project can be divided in two parts, the first on feature extraction and the second on classification and clustering.
+In more details, we applied various dimensionality reduction methods such as Latent Dirichlet Allocation (LDA) or Non-negative Matrix Factorisation (NMF) to embed the reviews into a geometrical space.
+We then decided to compare both supervised approaches such as Multinomial Regression and unsupervised approaches, using the Walktrap algorithm, to the problem of classification on the Yelp dataset.
 %------------------------------------------------
@@
 \centering
-\includegraphics[width=0.8\linewidth]{LDA.png}
+\includegraphics[width=0.8\linewidth]{img/LDA.png}
 \caption{Graphical Model Representation of LDA}
@@
 \State Sample a batch $\mathcal{S}$ of documents of size S
+\For{$t$=0 to $|D|/|\mathcal{S}|$}
 \For {$d$ in $\mathcal{S}$}
@@
 \State $\boldsymbol{\lambda} = (1-\rho_t)\boldsymbol{\lambda}+\rho_t\boldsymbol{\tilde{\lambda}}$
-\State $t = t+1$
-\State \textbf{goto} 3 and repeat until all documents are observed.
+\EndFor
 \end{algorithmic}
@@
 \centering
-\includegraphics[width=1\linewidth]{V.png}
+\includegraphics[width=1\linewidth]{img/V.png}
 \caption{Cross Validation over the number of Topics}
@@
 \centering
-\includegraphics[width=1\linewidth]{topics.png}
+\includegraphics[width=1\linewidth]{img/topics.png}
 \caption{Topics extracted from the Las Vegas reviews using OVI}
@@
 \section{Supervised Classification}
+
+Once the feature have been extracted, we can apply supervised learning methods to classify the Yelp restaurants considering the category labels as output.
+Several approaches are possible to solve this multi-labels classiffication task depending on the nature and patterns of the features.
+
+\subsection{Approach}
+
+The features are divided into two main parts: on one hand, the topics assignements extracted from the reviews with the LDA and on the other hand, the properties provided by Yelp.
+Pre-processing the latter part provided a 198 dimensional vector.
+These features contain both numerical values (rating, space coordinates, number of reviews, customer check-in...) and categorical ones which we converted into indicator variables.\\
+
+Given our numerical features, many different discriminative and generative models could be appllied on our data.
+Nonetheless, the indicator features are sparse and the data are really noisy.
+We need to consider a penalized or aggregated model to reduce overfitting.\\
+
+We chose a one-vs-all approach to tackle this multi-labels task where we build one binary classifier for each label.
+We then assign to the entries the labels predicted by each model.
+The goal is here to explore how the different models perform and to tune them to come up with the best estimator.
+We developped our own l2 penalized logistic regression and used sklearn for the other models.
+
+\subsection{Results}
+
+\paragraph{Dimensionality Reduction}
+
+We decided to reduce the dimension of the dataset before applying our model.
+We used it only on the customer check-ins counts to embed them in an euclidean space.
+We chose to project them because they already shared a common structure.
+Then, the combination of the embedded features with the latent features provided by the reviews is more consistent.
+We chose to apply it while keeping \textbf{95\%} of the variance which reduces the dimension from \textbf{168} to \textbf{19}.
+
+\paragraph{Models Evaluation}
+
+Here we provide the different results we obtained from our models.
+We ran one-vs-one classifiers for the 10 different labels which are the most represented in the Las Vegas restaurants.
+Then we evaluated for each classifier its accuracy and averaged them to get the evaluation metric printed in the table.
+We tested them on three different kinds of features provided by the reviews depending on the method used to build them.
+Then we ran each model on the PCA projection and on the raw data.
+We provided for comparaison the baseline model where we do not assign any label.
+This result is really high because of the skewness of the considered sample, among the 10 categories considered for 3822 restaurants the most represented (Fast Food) contains 553 entries and the least (American New) 280 entries.
+
+\begin{figure}[H]
+\begin{center}
+    \begin{tabular}{| l | l | l | l |}
+    \hline
+    & OVI LDA & GS LDA & NMF \\ \hline
+    Baseline: all False & 90,02 \% &  90.02 \% &  90.02 \% \\ \hline
+    Kernel rbf SVM & 90,81\% &  90.38\% &  90.38\% \\ \hline
+    Kernel rbf SVM + PCA & 90.83\% &  90.60\% &  90.57\% \\ \hline
+    Logistic Regression & 90.84\% &  91.89\%  &  91.24\%\\ \hline
+    Logistic Regression + PCA & 92.59\% &  92.53\% &  92.68\% \\ \hline
+    Lasso & 90.82\% &  93.44\% &  92.01\% \\ \hline
+	Lasso + PCA & 93.44\%  &  \textbf{94.46} \%  &  93.08\% \\ \hline
+    Random Forest & 92.12\% &  93.58\% &  93.37\% \\ \hline
+    Random Forest + PCA & 92.84\% &  94.66\% &  94.06\% \\ \hline
+    \end{tabular}
+\end{center}
+\caption{Classification results for different features}
+\end{figure}
+
+The first learning of this comparative study is the differences between each kind of feature.
+The models built with the GS features seems to outperform on average the two other which perform similarly to each other.
+These results are not surprising as the variationnal inference learns the closest model to the underlying one in terms of KL divergence.
+With the Gibbs sampling approach, we approximate the true underlying distribution at each iteration to refine our estimator.
+As a result, the latter method is by nature better to find the best model as long as it has enough iteration to converge and there actually exists an underlying mixture models.
+Nevertheless, the OVI remains a good proxy with regard to its time execution (53s against 50min for the Gibbs Sampler).\\
+
+Then, if we compare the models to each other.
+The support vector machine performs poorly, the linear version was even closer to the baseline.
+This confirms that the data are not linearly separable and even their projection by the rbf function used in sklearn library (gamma function) is quite impossible to separate.
+The logistic regression performs better under the l1 penalization because of our sparse feature.
+Lastly, the random forest managed to reduce the common overfitting of the decision trees while aggregating them and provides on the PCA projection a very good estimator.\\
+
+We plotted here the ROC curves of the Random forest for the 10 classes considered.
+The ranking of the area under the curve is almost the same that the descending ranking by number of positive elements for each classe.This shows that the more positive elements we have the better classifies the model.
+Nonethelless, trying to learn the model on a smaller and more balanced train set for the classes with a low number of positive elements does not improve the classification accuracy.
+
+\begin{figure}[H]
+	\includegraphics[scale=0.55]{img/roc_rf.png}
+	\centering
+	\caption{Roc curve for the Random Forest one-vs-all classifiers}
+\end{figure}
+
+TODO: analysis on the ROC curves
+
+\paragraph{Feature Importance}
+
+Once we found a sufficiantly good estimator, we can investigate the weights it assigns to each feature.
+This could provide an answer to two important questions: \textit{Are the feature extracted from the reviews more relevant than the one provided by Yelp to classify the restaurants by category?
+Among the features extracted by the review, can we identify for each category one or several highly discriminative features?} Moreover, we can compare the performance of the two different LDA we used.\\
+
+We answer these questions with a comparative study on four specific categories (Fast Food, Pizza, Nightlife and Bars) with a Random Forest on four kinds of features, depending on the type of LDA used and the reduction with a PCA.
+The results with the features built with an NMF are similar to those with the OVI.
+We used the measure provided by scikit learn to evaluate the importance of the features.
+It is defined as the total decrease in node impurity averaged over all trees of the ensemble.
+
+\begin{figure}[H]
+\centering
+\subfigure{
+\includegraphics[scale=0.24]{img/fast_food_ovi.png}
+}
+\quad
+\subfigure{
+\includegraphics[scale=0.24]{img/pizza_ovi.png}
+}
+\subfigure{
+\includegraphics[scale=0.24]{img/nightlife_ovi.png}
+}
+\quad
+\subfigure{
+\includegraphics[scale=0.24]{img/bars_ovi.png}
+}
+%
+\caption{Importance of the OVI LDA features in the one-vs-all Random Forest classification}
+\label{fig:figure}
+\end{figure}
+
+\begin{figure}[H]
+\centering
+\subfigure{
+\includegraphics[scale=0.24]{img/fast_food_ovi_pca.png}
+}
+\quad
+\subfigure{
+\includegraphics[scale=0.24]{img/pizza_ovi_pca.png}
+}
+\subfigure{
+\includegraphics[scale=0.24]{img/nightlife_ovi_pca.png}
+}
+\quad
+\subfigure{
+\includegraphics[scale=0.24]{img/bars_ovi_pca.png}
+}
+%
+\caption{Importance of the OVI LDA features with PCA in the one-vs-all Random Forest classification}
+\label{fig:figure}
+\end{figure}
+
+\begin{figure}[H]
+\centering
+\subfigure{
+\includegraphics[scale=0.24]{img/fast_food_gs.png}
+}
+\quad
+\subfigure{
+\includegraphics[scale=0.24]{img/pizza_gs.png}
+}
+\subfigure{
+\includegraphics[scale=0.24]{img/nightlife_gs.png}
+}
+\quad
+\subfigure{
+\includegraphics[scale=0.24]{img/bars_gs.png}
+}
+%
+\caption{Importance of the GS LDA features in the one-vs-all Random Forest classification}
+\label{fig:figure}
+\end{figure}
+
+\begin{figure}[H]
+\centering
+\subfigure{
+\includegraphics[scale=0.24]{img/fast_food_gs_pca.png}
+}
+\quad
+\subfigure{
+\includegraphics[scale=0.24]{img/pizza_gs_pca.png}
+}
+\subfigure{
+\includegraphics[scale=0.24]{img/nightlife_gs_pca.png}
+}
+\quad
+\subfigure{
+\includegraphics[scale=0.24]{img/bars_gs_pca.png}
+}
+%
+\caption{Importance of the GS LDA features with PCA in the one-vs-all Random Forest classification}
+\label{fig:figure}
+\end{figure}
+
+\begin{figure}[H]
+\centering
+\includegraphics[width=1\linewidth]{img/gs_topics.png}
+\caption{Topics extracted from the Las Vegas reviews using GS}
+\end{figure}
+
+First, considering the results for the OVI features, we observe that some properties provided by Yelp are discriminative for our classification.
+For example, the attribute \textit{Good for Kids} helps to sort the Bars and the Nightlife categories which is not surprising.
+The Fast Food may be the restaurants with the largest number of reviews as they have the largest number of customers, the model confirms this with the high weight on the \textit{reviews\_count}.
+This is also a cheap restaurant, hence the importance of the price range.
+As a result, it is worth considering the features provided by Yelp as they help discriminate the entries.\\
+
+Second, for the categories Pizza with the features extracted by the OVI we observe a discriminative feature which matchs the one about Pizza provided in the figure 3.
+Then, for the same LDA method, there is no discriminative feature for the other categories.
+Now, if we consider the results for the GS features, each category has a highly discriminative feature.
+Moreover, if we look at the most common words for each of these topics in the figure 10, we naturally understand their importance in the classification.
+This result confirms our analysis on the models.
+The Gibbs sampling method provides a finer topic distribution over the documents (here it is a labels distribution over the restaurants).
+
+Lastly, it is worth noticing the effect of the PCA on the importance of the features.
+For both the OVI and the GS, if we consider the category pizza, the results with the PCA are much more clear-cut.
+The weight of the most important feature and its difference with those of the other features are higher.
+We can explain this because the projection gives more structure to the data and reduces the noise.\\
+
+This part was about confronting our data to supervised methods to grasp their patterns and also coming up with a good classification.
+We provided empirical results to confirm the difference between the two most common LDA methods and proved that with the Gibbs sampling, the LDA can be really efficient to find the underlying topics of a set of documents, being much butter than a matrix factorization method.
+Related to our problem, it shows us that the features contain some information, but the LDA features remain more important to find the labels of a restaurant.
 
@@
 
-Running the algorithm from the \emph{igraph} in R, we outputted a dendogram (cf.
+We ran the algorithm from the \emph{igraph} package in R on the three graphs generated with the three approaches mentionned above (NMF, OVI LDA, GS LDA).
+The results where extremely similar.
+We outputted a dendogram (cf.
 Figure 3) representing the obtained clustering.
@@
 It is not yet entirely clear to us how to get the optimum number of clusters.
-We were puzzled to see that the Walktrap algorithm indicated that a cut into 3 big clusters represented the optimum partition.
+We were puzzled to see that the Walktrap algorithm indicated that a cut into three big clusters represented the optimum partition.
 Knowing the structure of the sampled restaurants, we decided to further investigate the dendogram.
-As one can see on Figure 3, cutting the tree at different heights, we can obtain 5 clear colored communities, corresponding to 5 of the 6 tags we pre-selected.\\
+As one can see on Figure 3, cutting the tree at different heights, we can obtain five clear colored communities, corresponding to five of the six tags we pre-selected.\\
 
@@
 \centering
-\includegraphics[width=1\linewidth]{confusion}
+\includegraphics[width=1\linewidth]{img/confusion}
 \caption{Confusion Matrix using the Walktrap Algorithm}
@@
 \centering
-\includegraphics[angle=90,width=0.25\linewidth]{den_ovi2-1.png}
+\includegraphics[angle=90,width=0.25\linewidth]{img/den_ovi2-1.png}
 \caption{Dendogram outputted by the Walktrap Algorithm}
@@
 \section{Next steps}
+
+So far, we managed to extract the categories of the restaurants as latent features with a latent dirichlet allocation algorithm on the aggregated reviews for each restaurant. \\
+
 Futur work could focus on the sub-cliques and try to get a finer classification by combining them with other features like check-ins, parking availability, etc.
-As a variant, we could also try a supervised LDA, where we use the existing categories as a response variable associated with each document and infer the joint model of the documents and the responses.
+As a variant, we could also try a supervised LDA, where we use the existing categories as a response variable associated with each document and infer the joint model of the documents and the responses.\\
+
+As a variant, we could try a supervised LDA, where we use the existing categories as a response variable associated with each document and infer the joint model of the documents and the responses.
+Lastly, this method is applicable on each review separately to predict the rating of the review, with a supervised lda also to avoid the predominance of the categories in the topics.
 

### 2015-12-12 paper/article_2.tex
changes to the paper + abstract

@@
 
-We planned on building latent features from the text reviews which would depict the cat- egories of the business.
-To put it in a nutshell, we would like to build from the text reviews of an entry a vector representation which carries local geometry information.
-Once we built the document-term matrix containing the words count of the reviews for each business (the reviews are aggregated over each restaurant), we could simply use a matrix factorisation on the counts .
-To be able to interpret the latent features as topics, we could use a Non-negative matrix factorization (the possible negative features in the SVD cannot stand for cluster as- signement).
-A finer result can be reached with the use of a generative probabilistic model, that’s why we chosed the latent dirichlet allocation.
-The LDA uses a Dirichlet prior on the words distribution over the topics and on the topics distribution over the document which will gives them more freedom than the deterministic approach of the NMF.
+Our objective is to improve the categorization system of the Yelp businesses using machine learning techniques.
+To achieve our goal, we extract significant information out of the text reviews posted on Yelp using our own coded-up Latent Dirichlet Allocation (LDA) using Online Variational Inference, and benchmark it with an LDA using Gibbs Sampling and Non Negative Matrix Factorisation.
+We then present two methods for classifying restaurants.
+We first resorted to a supervised approach with a multinomial logistic regression on  the text reviews combined with characteristic features of businesses - such as localisations, prices, customer type or check-in data.
+The second approach is unsupervised, using the Walktrap Algorithm, a community detection algorithm on network of restaurant.
+If the different feature extraction methods (LDA, NMF) performed differently for the supervised and unsupervised approach, we observed some very promising results.
+The results could be used as the first step to an automated categorization system on the Yelp website.
 
@@
 As part of the Yelp Data Set Challenge Round 6, we decided to tackle the issue of classification with ultimate objective to be able to create an automatised method to classify venues, based on the information contained on the business' web page and most importantly the written reviews from Yelpers.
-\\
 
-This project can be divided in two parts, the first on feature extraction and the second on classification and clustering.
+\noindent This project can be divided in two parts, the first on feature extraction and the second on classification and clustering.
 In more details, we applied various dimensionality reduction methods such as Latent Dirichlet Allocation (LDA) or Non-negative Matrix Factorisation (NMF) to embed the reviews into a geometrical space.
@@
 %------------------------------------------------
-
+\columnbreak
 \section{Data}
@@
 
-We would like to also make a general comment about the Online Variational algorithm.
+\noindent We would like to also make a general comment about the Online Variational algorithm.
 We noticed that the OVI algorithm is extremely sensitive to the hyperparametrisation, i.e the batch size $S$, the forgetfullness parameter $\kappa$ and the early iterations weith parameter $\tau$.
@@
 
-We now present two different approaches to answer the question of classification using supervised and unsupervised machine learning.\\
+\noindent We now present two different approaches to answer the question of classification using supervised and unsupervised machine learning.\\
 
@@
 
-Once the feature have been extracted, we can apply supervised learning methods to classify the Yelp restaurants considering the category labels as output.
-Several approaches are possible to solve this multi-labels classiffication task depending on the nature and patterns of the features.
+Once the features have been extracted, we can apply supervised learning methods to classify the Yelp restaurants considering the category labels as output.
+Several approaches are possible to solve this multi-label classiffication task depending on the nature and patterns of the features.
 
@@
 
-The features are divided into two main parts: on one hand, the topics assignements extracted from the reviews with the LDA and on the other hand, the properties provided by Yelp.
+\noindent The features are divided into two main parts: on one hand, the topics assignements extracted from the reviews with the LDA and on the other hand, the properties provided by Yelp.
 Pre-processing the latter part provided a 198 dimensional vector.
-These features contain both numerical values (rating, space coordinates, number of reviews, customer check-in...) and categorical ones which we converted into indicator variables.\\
+These features contained both numerical values (rating, space coordinates, number of reviews, customer check-in...) and categorical ones which we converted into indicator variables.\\
 
-Given our numerical features, many different discriminative and generative models could be appllied on our data.
+\noindent Given our numerical features, many different discriminative and generative models could be appllied on our data.
 Nonetheless, the indicator features are sparse and the data are really noisy.
-We need to consider a penalized or aggregated model to reduce overfitting.\\
+We therefore needed to consider a penalized or aggregated model to reduce overfitting.\\
 
-We chose a one-vs-all approach to tackle this multi-labels task where we build one binary classifier for each label.
+\noindent We chose a one-vs-all approach to tackle this multi-label task, and built one binary classifier for each label.
 We then assign to the entries the labels predicted by each model.
 The goal is here to explore how the different models perform and to tune them to come up with the best estimator.
-We developped our own l2 penalized logistic regression and used sklearn for the other models.
+We developped our own L2 penalized logistic regression and used sklearn for the other models.
 
@@
 
-We decided to reduce the dimension of the dataset before applying our model.
-We used it only on the customer check-ins counts to embed them in an euclidean space.
-We chose to project them because they already shared a common structure.
-Then, the combination of the embedded features with the latent features provided by the reviews is more consistent.
-We chose to apply it while keeping \textbf{95\%} of the variance which reduces the dimension from \textbf{168} to \textbf{19}.
+\noindent We decided to reduce the dimension of the dataset before fitting our model.
+As the high-dimensionality is largely due to the customer check-in counts and as they share a common structure, we decided to project them in an euclidean space.
+The combination of the embedded features with the latent features provided by the reviews is more consistent.
+We apply a principal component analysis (PCA) while keeping \textbf{95\%} of the variance which reduces the dimension from \textbf{168} to \textbf{19}.
 
@@
 
-Here we provide the different results we obtained from our models.
+\noindent Here we provide the different results we obtained from our models.
 We ran one-vs-one classifiers for the 10 different labels which are the most represented in the Las Vegas restaurants.
@@
 Then we ran each model on the PCA projection and on the raw data.
-We provided for comparaison the baseline model where we do not assign any label.
+We also show for comparaison the baseline model where we do not assign any label.
 This result is really high because of the skewness of the considered sample, among the 10 categories considered for 3822 restaurants the most represented (Fast Food) contains 553 entries and the least (American New) 280 entries.
@@
 
-The first learning of this comparative study is the differences between each kind of feature.
-The models built with the GS features seems to outperform on average the two other which perform similarly to each other.
+\noindent The first outcome of this comparative study is the differences between each feature extraction method.
+The model built with the GS features seems to outperform on average the other two, which perform similarly to each other.
 These results are not surprising as the variationnal inference learns the closest model to the underlying one in terms of KL divergence.
@@
 
-Then, if we compare the models to each other.
-The support vector machine performs poorly, the linear version was even closer to the baseline.
-This confirms that the data are not linearly separable and even their projection by the rbf function used in sklearn library (gamma function) is quite impossible to separate.
-The logistic regression performs better under the l1 penalization because of our sparse feature.
+\noindent If we then compare the models to each other, we see that the support vector machine performs poorly and that the linear version was even closer to the baseline.
+This confirms that the data is not linearly separable and even their projection by the rbf function used in sklearn library (gamma function) is quite impossible to separate.
+The logistic regression performs better under the l1 penalization because of the sparsity of our features.
 Lastly, the random forest managed to reduce the common overfitting of the decision trees while aggregating them and provides on the PCA projection a very good estimator.\\
 
-We plotted here the ROC curves of the Random forest for the 10 classes considered.
-The ranking of the area under the curve is almost the same that the descending ranking by number of positive elements for each classe.This shows that the more positive elements we have the better classifies the model.
-Nonethelless, trying to learn the model on a smaller and more balanced train set for the classes with a low number of positive elements does not improve the classification accuracy.
+\noindent We plotted here the ROC curves of the Random forest for the 10 classes considered.
+The ranking with respect to the area under the curve is very close to the one induced by the number of positive elements for each class.This shows that the more positive elements we have, the better the model actually performs.
+Nonetheless, trying to learn the model on a smaller and more balanced train set for the classes with a low number of positive elements does not improve the classification accuracy.
 
@@
 
-TODO: analysis on the ROC curves
-
 \paragraph{Feature Importance}
 
-Once we found a sufficiantly good estimator, we can investigate the weights it assigns to each feature.
-This could provide an answer to two important questions: \textit{Are the feature extracted from the reviews more relevant than the one provided by Yelp to classify the restaurants by category?
+\noindent Once we found a sufficiantly good estimator, we investigated the weights it assigned to each feature.
+This provided an answer to two important questions: \textit{Are the feature extracted from the reviews more relevant than the one provided by Yelp to classify the restaurants by category?
 Among the features extracted by the review, can we identify for each category one or several highly discriminative features?} Moreover, we can compare the performance of the two different LDA we used.\\
 
-We answer these questions with a comparative study on four specific categories (Fast Food, Pizza, Nightlife and Bars) with a Random Forest on four kinds of features, depending on the type of LDA used and the reduction with a PCA.
+\noindent We answer these questions with a comparative study on four specific categories (Fast Food, Pizza, Nightlife and Bars) with a Random Forest on four kinds of features, depending on the type of LDA used and the reduction with PCA.
 The results with the features built with an NMF are similar to those with the OVI.
@@
 
-First, considering the results for the OVI features, we observe that some properties provided by Yelp are discriminative for our classification.
+\noindent First, considering the results for the OVI features, we observe that some properties provided by Yelp are discriminative for our classification.
 For example, the attribute \textit{Good for Kids} helps to sort the Bars and the Nightlife categories which is not surprising.
@@
 
-Second, for the categories Pizza with the features extracted by the OVI we observe a discriminative feature which matchs the one about Pizza provided in the figure 3.
+\noindent Second, for the Pizza category with the features extracted by the OVI we observe a discriminative feature which matchs the one about Pizza provided in the figure 3.
 Then, for the same LDA method, there is no discriminative feature for the other categories.
@@
 This result confirms our analysis on the models.
-The Gibbs sampling method provides a finer topic distribution over the documents (here it is a labels distribution over the restaurants).
+The Gibbs sampling method provides a finer topic distribution over the documents (here it is a label distribution over the restaurants).
 
-Lastly, it is worth noticing the effect of the PCA on the importance of the features.
-For both the OVI and the GS, if we consider the category pizza, the results with the PCA are much more clear-cut.
+\noindent Lastly, it is worth noticing the effect of the PCA on the feature importance.
+For both the OVI and the GS, if we look back at the Pizza category, the results with the PCA are much more clear-cut.
 The weight of the most important feature and its difference with those of the other features are higher.
-We can explain this because the projection gives more structure to the data and reduces the noise.\\
+We can explain this by the fact that the projection gave more structure to the data and reduces the noise.\\
 
-This part was about confronting our data to supervised methods to grasp their patterns and also coming up with a good classification.
-We provided empirical results to confirm the difference between the two most common LDA methods and proved that with the Gibbs sampling, the LDA can be really efficient to find the underlying topics of a set of documents, being much butter than a matrix factorization method.
-Related to our problem, it shows us that the features contain some information, but the LDA features remain more important to find the labels of a restaurant.
+\noindent This part was about confronting our data to supervised methods to grasp their patterns and also coming up with a good classification.
+We provided empirical results to confirm the difference between the two common LDA methods and proved that with the Gibbs sampling, the LDA can be really efficient at finding the underlying topics on a set of documents.
+It also proved that it performed much butter than a matrix factorization method.
+Related to our problem, it showed us that if numerical features provided by Yelp contained some information, the LDA features remained much more important when looking to find the labels of a restaurant.
 

### 2015-12-12 paper/article_2.tex
final paper

@@
 \renewcommand{\abstracttextfont}{\normalfont\small\itshape} % Set the abstract itself to small italic text
+\usepackage[toc,page]{appendix}
 
@@
 Our objective is to improve the categorization system of the Yelp businesses using machine learning techniques.
-To achieve our goal, we extract significant information out of the text reviews posted on Yelp using our own coded-up Latent Dirichlet Allocation (LDA) using Online Variational Inference, and benchmark it with an LDA using Gibbs Sampling and Non Negative Matrix Factorisation.
+To achieve our goal, we extract significant information out of the text reviews posted on Yelp using our own coded-up Latent Dirichlet Allocation (LDA) using online variational inference (OVI), and benchmark it with the LDA using a Gibbs samplingmethod (GS) and the Non Negative Matrix Factorisation (NMF).
 We then present two methods for classifying restaurants.
-We first resorted to a supervised approach with a multinomial logistic regression on  the text reviews combined with characteristic features of businesses - such as localisations, prices, customer type or check-in data.
+We first resorted to a supervised approach with a one-vs-all classifiers on  the text reviews combined with characteristic features of businesses - such as localisations, prices, customer type or check-in counts.
 The second approach is unsupervised, using the Walktrap Algorithm, a community detection algorithm on network of restaurant.
-If the different feature extraction methods (LDA, NMF) performed differently for the supervised and unsupervised approach, we observed some very promising results.
+If the different feature extraction methods performs differently for the supervised and unsupervised approach, we observe some very promising results.
 The results could be used as the first step to an automated categorization system on the Yelp website.
@@
 \lettrine[nindent=0em,lines=1]{T}he classification system in Yelp is manual.
-When the owner of a business creates a page for his restaurant or bar, he is asked to enter a certain number of attributes or "tags".
-Yelp users can then alter or even add some new tags based on their experiences.
-As part of the Yelp Data Set Challenge Round 6, we decided to tackle the issue of classification with ultimate objective to be able to create an automatised method to classify venues, based on the information contained on the business' web page and most importantly the written reviews from Yelpers.
+When the owner of a business creates a page for his restaurant or bar, he is can provide a certain number of labels.
+Yelp users can then alter or even add new tags based on their experiences.
+As part of the Yelp Data Set Challenge Round 6, we decided to tackle the issue of entries classification.
+Our ultimate objective is to create an automatised method to classify the businesses, based on their properties and most importantly on their reviews from Yelpers.
+\\
 
-\noindent This project can be divided in two parts, the first on feature extraction and the second on classification and clustering.
-In more details, we applied various dimensionality reduction methods such as Latent Dirichlet Allocation (LDA) or Non-negative Matrix Factorisation (NMF) to embed the reviews into a geometrical space.
-We then decided to compare both supervised approaches such as Multinomial Regression and unsupervised approaches, using the Walktrap algorithm, to the problem of classification on the Yelp dataset.
+This project can be divided in three parts.
+First, to extract feature, we applied various dimensionality reduction methods such as Latent Dirichlet Allocation (LDA) or Non-negative Matrix Factorisation (NMF) to embed the reviews into a geometrical space.
+Then, we applied supervised learning methods to evaluate how relevant are the feature to predict the labels.
+Last, we built an unsupervised clustering method using the Walktrap algorithm.
+
 %------------------------------------------------
@@
 \begin{compactitem}
-	\item 1.6 million reviews
-	\item 61 000 businesses		
-	\item 481 000 attributes 
-	\item aggregated check-in measurements over time
+    \item 1.6 million reviews;
+    \item 61 000 businesses;    
+    \item 481 000 attributes; 
+    \item 168 customer check-in counts, corresponding to the average number of checkins per hour per day of the week.
 \end{compactitem}
@@
 \noindent For simplicity, we chose to focus on restaurants and bars in the city of Las Vegas, Nevada.
-We reduced the data to a dataset of 3822 businesses, about 20 thousands reviews and 250 other features such as hours, parking availabity, take-out, ambience.
-If the numerical data we received from Yelp was mostly cleaned, it was not the case of the text data.
+This reduced the data to a dataset of 3822 businesses, with about 20 thousands reviews and 250 other features per entry such as hours, parking availabity, take-out, ambience.
+If the numerical data provided by Yelp is mostly cleaned, it was not the case of the text data.
 Cleaning the reviews represented a significant part of this final project.
@@
 \begin{compactitem}
-	\item We aggregated all the reviews about a particular business into a "super" review, in order to get a general sense of what the restaurant was about,
-	\item We applied spelling corrections, removed common stopwords and generic words such as "table" or "restaurants",
-	\item We attempted at only selecting common words and not adjectives in order to focus on what the venues were about and not the users' opinions,
-	\item We transformed the corpus of "super reviews" into a document-term matrix that we could exploit.
+    \item We aggregated all the reviews about a particular business into a "super" review, in order to get a general sense of what the restaurant was about;
+    \item We applied spelling corrections, removed common stopwords and generic words such as "table" or "restaurants";
+    \item We attempted at only selecting common words and not adjectives in order to focus on what the venues were about and not the users' opinions (this process was done taking advantage of Spark to reduce the computing time);
+    \item We transformed the corpus of "super reviews" into a document-term matrix that we could exploit;
+    \item As we aggregated the reviews, some words may be more prevalent than others, so we scaled the words counts into the range [0, 100] for each review.
 \end{compactitem}
@@
 
-To extract content from the reviews, we applied 2  methods from Topic Modeling to reduce the document term matrix into meaningful information.
-We first looked at LDA, using both a Gibbs sampler and Online Variational Inference (OVI) algorithm.
-Note that we used the Gibbs sampler as a way to benchmark our coded OVI.
+To extract content from the reviews, we applied two methods from topic modeling to reduce the document term matrix into meaningful information.
+We first looked at LDA, using both a Gibbs sampler (GS) and an Online Variational Inference (OVI) algorithm.
+Note that we used the Gibbs sampler as a way to benchmark our own version of OVI.
 The motivation behind OVI is twofold.
 First, it appeared more appropriate to the data we were working with, indeed new reviews can always be added to the corpus in continuous flow.
-Second, it showed some extremely significant time improvement over the Gibbs sampler version in Python (cf figure 1).
-We also wanted to compare the performance of LDA with a non-probabilistic approach which is NMF.
+Second, it showed some extremely significant time improvement over the Gibbs sampler version in Python.
+We also wanted to compare the performance of LDA with a non-probabilistic approach which is the NMF.
 
@@
 The LDA is a three-level hierarchical Bayesian model.
-The basic idea that documents are represented as random mixtures over latent topics and each topic is characterized by a distribution over words.\cite{LDA}\\
+The basic idea is that documents are represented as random mixtures over latent topics and each topic is characterized by a distribution over words.\cite{LDA}\\
 
@@
 
-\subsection{Parameter Estimation and algorithm:}
+\subsection{Inference}
 
@@
 Alternatively, we chose the online variational inference method which finds the variational parameters that optimize a lower bound on the loglikelihood.
-The setup \cite{OLLD} of the Variational Inference is as follows.
+The setup \cite{OLLD} of the variational inference is as follows.
 We first approximate the true posterior by a simpler and factorised distribution:
+
 $$q(\boldsymbol{z},\boldsymbol{\theta},\boldsymbol{\beta}) = q(\boldsymbol{z})q(\boldsymbol{\theta})q(\boldsymbol{\beta}) $$
@@
 \noindent The $\boldsymbol{\gamma}$ parameter rule the topic assignments for each document and the $\boldsymbol{\lambda}$, the topics themselves.
-We then minimise the KL divergence between the distribution $q$ and the true posterior $p$ like for the usual variational inference.
-What differs in online variational inference is that we sample a batch of document at each step and perform the E-step as if this batch constituted the entire corpus.
+We then minimise the KL divergence between the distribution $q$ and the true posterior $p$.
+What differs in the online variational inference is that we sample a mini-batch of document at each step and perform the E-step as if this mini-batch constituted the entire corpus.
 We present the algorithm below:
@@
 \begin{algorithm}[H]
-\caption{Batched Online Variational Inference}\label{euclid}
+\caption{Minibatch Online Variational Inference}\label{euclid}
 \begin{algorithmic}[1]
@@
 \noindent where $\kappa \in (0.5,1]$ rules how fast we forget old values of $\tilde{\lambda}$ and $\tau_{0}$ how much weight one wants to put on the first iterations.
+$\alpha$ and $\eta$ where fixed at the same value $\frac{1}{|D|}$.
 
@@
 We need a measure to evaluate the performance of our model and to tune the hyperparameters.
-We use perplexity on held-out data as a measure of our model fit.
-Perplexity is defined as the geometric mean of the log likelihood of the words in the held-out set of docuements given the trained model.
-In our case, for each document we held out 20\% of the words which constitue the test set.
+We use the perplexity on held-out data as a measure of our model fit.
+The perplexity is defined as the geometric mean of the log likelihood of the words in the held-out set of documents given the trained model.
+In our case, for each document we held out 20\% of the words which constitue the validation set to apply a 5-fold cross-validation.
 
@@
 
-\noindent We used this measure to optimize the number of topics K and the hyper parameters of the optimization.
+\noindent We used this measure to optimize the number of topics K and the hyper parameters $\kappa$, $\tau$ of the optimization.
 We also used the perplexity on the training set to benchmark our algorithm with the Gibbs sampler in the LDA 1.0.3 package in Python:
@@
 \includegraphics[width=1\linewidth]{img/V.png}
-\caption{Cross Validation over the number of Topics}
+\caption{5-fold Cross Validation over the number of Topics}
 \end{figure}
@@
 
-\noindent We would like to also make a general comment about the Online Variational algorithm.
-We noticed that the OVI algorithm is extremely sensitive to the hyperparametrisation, i.e the batch size $S$, the forgetfullness parameter $\kappa$ and the early iterations weith parameter $\tau$.
+We would like to make a general comment about the online variational algorithm.
+We noticed that its algorithm is extremely sensitive to the hyperparametrisation, i.e the batch size $S$, the forgetfullness parameter $\kappa$ and the early iterations weith parameter $\tau$.
 This was also noted by Tamara Broderick, Nicholas Boyd, Andre Wibisono and Ashia C.
 Wilson in their paper\cite{svi}.
-In addition to validating the number of topics, validating over these parameters was crucial to obtain valuable resutls.\\
+In addition to validating the number of topics, validating over these parameters was crucial to obtain valuable results.\\
 
-\noindent We now present two different approaches to answer the question of classification using supervised and unsupervised machine learning.\\
+We now present two different approaches to answer the question of classification using supervised and unsupervised machine learning methods.\\
 
 %------------------------------------------------
-\section{Supervised Classification}
+\section{Classification}
 
@@
 The goal is here to explore how the different models perform and to tune them to come up with the best estimator.
-We developped our own L2 penalized logistic regression and used sklearn for the other models.
+We developped our own L2 penalized logistic regression and used \emph{scikit-learn} \cite{sklearn} for the other models.
 
@@
     Baseline: all False & 90,02 \% &  90.02 \% &  90.02 \% \\ \hline
-    Kernel rbf SVM & 90,81\% &  90.38\% &  90.38\% \\ \hline
-    Kernel rbf SVM + PCA & 90.83\% &  90.60\% &  90.57\% \\ \hline
-    Logistic Regression & 90.84\% &  91.89\%  &  91.24\%\\ \hline
-    Logistic Regression + PCA & 92.59\% &  92.53\% &  92.68\% \\ \hline
-    Lasso & 90.82\% &  93.44\% &  92.01\% \\ \hline
-	Lasso + PCA & 93.44\%  &  \textbf{94.46} \%  &  93.08\% \\ \hline
+    Kernel rbf SVM & 91.00\%  &  90.73\%  &  90.67\% \\ \hline
+    Kernel rbf SVM + PCA & 90.62\%  &  90.85\%  &  90.85\% \\ \hline
+    Logistic Regression & 91.39\%  &  91.86\%  &  91.86\%\\ \hline
+    Logistic Regression + PCA & 92.37\%  &  92.89\%  &  93.16\% \\ \hline
+    Lasso & 91.18\%  &  93.75\%  &  92.40\% \\ \hline
+	Lasso + PCA & 92.53\%  &  94.83\%  &  93.35\% \\ \hline
     Random Forest & 92.12\% &  93.58\% &  93.37\% \\ \hline
-    Random Forest + PCA & 92.84\% &  94.66\% &  94.06\% \\ \hline
+    Random Forest + PCA & 92.84\% &  \textbf{94.66} \% &  94.06\% \\ \hline
     \end{tabular}
@@
 The logistic regression performs better under the l1 penalization because of the sparsity of our features.
-Lastly, the random forest managed to reduce the common overfitting of the decision trees while aggregating them and provides on the PCA projection a very good estimator.\\
+Lastly, the random forest managed to reduce the common overfitting of the decision trees while aggregating them and provides on the PCA projection the best estimator.\\
 
@@
 
-Each restaurant is now represented as probability distribution over the latent topics.
-Using the Shannon distance (symmetric Kullback-Liebler Divergence), we created a distance matrix gathering information on how close 2 restaurants are based on their reviews.
+Each restaurant is now represented as a probability distribution over the latent topics.
+Using the Shannon distance (symmetric Kullback-Liebler Divergence), we created a distance matrix gathering information on how close two restaurants are based on their reviews.
 After many experimentations, we chose to transform this distance matrix into a weighted adjacency matrix:\\
@@
 
-\noindent The choice of having a non-zero weight between two restaurants even though they are not "close" is motivated by the fact that many graph clustering algorithm and in particular the WalkTrap algorithm that we used and present next, will only work on a connected graph.\\
+\noindent The choice of having a non-zero weight between two restaurants even though they are not "close" is motivated by the fact that many graph clustering algorithm, in particular the WalkTrap algorithms that we used, only work on a connected graph.\\
 
@@
 
-We ran the algorithm from the \emph{igraph} package in R on the three graphs generated with the three approaches mentionned above (NMF, OVI LDA, GS LDA).
+We ran the algorithm from the \emph{igraph} \cite{igr} package in R on the three graphs generated with the three approaches mentionned above (NMF, OVI LDA, GS LDA).
 The results where extremely similar.
 We outputted a dendogram (cf.
-Figure 3) representing the obtained clustering.
+Annex) representing the obtained clustering.
 We colored the tag of each business for a better readability.
@@
 We focused a bit more on these venues and explored manually the tags associated with them.
-We noticed that these Sports bar were most of the time having other tags such as "Restaurants","Bar", "American" and some even "Mexican".
+We noticed that these Sports bar have most of the time other tags such as "Restaurants","Bar", "American" and some even "Mexican".
 Reviews for these venues might have been misallocated due to the proximity of types of food, drinks or "ambiance" with Mexican restaurants.
-It is nonetheless interesting to note that were grouped almost all together inside the Mexican restaurants, and that if we cut the three at the sixth level then they would all be gathered in 2 cliques.\\
+It is nonetheless interesting to note that they were grouped almost all together inside the Mexican restaurants, and that if we cut the tree at the sixth level then they would all be gathered in 2 cliques.\\
 
@@
 It seems very unlikely to discover a restaurant that one can identify as both a Mexican and a Sushi place or even a Sushi place specialising in Breakfast (unless its speciality is the takagoyaki, a type of Japanese omelette made by "rolling together several layers of cooked egg").
-It was often the case that misclassified restaurant had the tag "Buffet" which is for our purpose of classification our worst ennemy as it will phagocytose many categories at once.
-
-\begin{figure*}
-\centering
-\includegraphics[angle=90,width=0.25\linewidth]{img/den_ovi2-1.png}
-\caption{Dendogram outputted by the Walktrap Algorithm}
-\end{figure*}
+It was often the case that misclassified restaurants had the tag "Buffet" which is for our purpose of classification our worst ennemy as it will phagocytose many categories at once.
 
@@
 \section{conclusion}
-By using a combination of unsupervised learning and graph theory, we managed to retrieve most of the original classification that is up to now still done by hand !
-This work could result in an automation tool for Yelp to label properly its database.
+
+This study illustrates different methods to extract feature from a set of documents.
+The results confirmed that the latent Dirichlet allocation manages to grasp the underlying features.
+The comparison with the supervised learning methods confirmed the importance of the feature extraction part in a machine learning problem.
+It also corroborates the assumption that the features of the businesses could be used to infer their category labels.
+Finally, the unsupervised clustering process we developped provides encouraging results and could result in an automation tool for Yelp to label properly its database.
 
@@
 
+\newpage
+
+\begin{figure*}
+\centering
+\includegraphics[angle=90,width=0.25\linewidth]{img/den_ovi2-1.png}
+\caption{Dendogram outputted by the Walktrap Algorithm}
+\end{figure*}
+
 \end{document}

### 2015-12-12 paper/article_2.tex

@@
     Lasso & 91.18\%  &  93.75\%  &  92.40\% \\ \hline
-	Lasso + PCA & 92.53\%  &  94.83\%  &  93.35\% \\ \hline
+	Lasso + PCA & 92.53\%  &  \textbf{94.83}\%  &  93.35\% \\ \hline
     Random Forest & 92.12\% &  93.58\% &  93.37\% \\ \hline
-    Random Forest + PCA & 92.84\% &  \textbf{94.66} \% &  94.06\% \\ \hline
+    Random Forest + PCA & 92.84\% &  94.66 \% &  94.06\% \\ \hline
     \end{tabular}
@@
 The logistic regression performs better under the l1 penalization because of the sparsity of our features.
-Lastly, the random forest managed to reduce the common overfitting of the decision trees while aggregating them and provides on the PCA projection the best estimator.\\
+Lastly, the random forest managed to reduce the common overfitting of the decision trees while aggregating them and provides on the PCA projection a very good estimator.\\
 

### 2015-12-24 paper/article_2.tex
final version
paper updates

@@
 \fancyfoot{} % Blank out the default footer
-\fancyhead[C]{Userless Classificaton for the Yelp Dataset Challenge} % Custom header text
+\fancyhead[C]{Userless Classification for the Yelp Dataset Challenge} % Custom header text
 \fancyfoot[RO,LE]{\thepage} % Custom footer text
@@
 
-\title{\vspace{-15mm}\fontsize{24pt}{10pt}\selectfont\textbf{Userless Classificaton for the Yelp Dataset Challenge}} % Article title
+\title{\vspace{-15mm}\fontsize{24pt}{10pt}\selectfont\textbf{Userless Classification for the Yelp Dataset Challenge}} % Article title
 
@@
 We then present two methods for classifying restaurants.
-We first resorted to a supervised approach with a one-vs-all classifiers on  the text reviews combined with characteristic features of businesses - such as localisations, prices, customer type or check-in counts.
+We first resorted to a supervised approach with one-vs-all classifiers on  the text reviews combined with characteristic features of businesses - such as localisations, prices, customer type or check-in counts.
 The second approach is unsupervised, using the Walktrap Algorithm, a community detection algorithm on network of restaurant.

### 2016-01-16 paper/article_2.tex
update report

@@
 \fancyfoot{} % Blank out the default footer
-\fancyhead[C]{Userless Classification for the Yelp Dataset Challenge} % Custom header text
+\fancyhead[C]{Userless Classification of the Yelp's Restaurants} % Custom header text
 \fancyfoot[RO,LE]{\thepage} % Custom footer text
@@
 
-\title{\vspace{-15mm}\fontsize{24pt}{10pt}\selectfont\textbf{Userless Classification for the Yelp Dataset Challenge}} % Article title
+\title{\vspace{-15mm}\fontsize{24pt}{10pt}\selectfont\textbf{Userless Classification of the Yelp's Restaurants}} % Article title
 
@@
 \normalsize Final Project for CS281, Harvard University \\ % Your institution
-\normalsize {nicolas.drizard@g.harvard.edu \quad vaudi@g.harvard.edu} % Your email address
+\normalsize {nicolasdrizard@g.harvard.edu \quad vaudi@g.harvard.edu} % Your email address
 \vspace{-5mm}
@@
 Our objective is to improve the categorization system of the Yelp businesses using machine learning techniques.
-To achieve our goal, we extract significant information out of the text reviews posted on Yelp using our own coded-up Latent Dirichlet Allocation (LDA) using online variational inference (OVI), and benchmark it with the LDA using a Gibbs samplingmethod (GS) and the Non Negative Matrix Factorisation (NMF).
+To achieve our goal, we extract significant information out of the text reviews posted on Yelp using our own coded-up Latent Dirichlet Allocation (LDA) using online variational inference (OVI), and benchmark it with the LDA using a Gibbs sampling method (GS) and the Non Negative Matrix Factorization (NMF).
 We then present two methods for classifying restaurants.
 We first resorted to a supervised approach with one-vs-all classifiers on the text reviews combined with characteristic features of businesses - such as localisations, prices, customer type or check-in counts.
-The second approach is unsupervised, using the Walktrap Algorithm, a community detection algorithm on network of restaurant.
-If the different feature extraction methods performs differently for the supervised and unsupervised approach, we observe some very promising results.
-The results could be used as the first step to an automated categorization system on the Yelp website.
+The second approach is unsupervised, using a community detection algorithm on the network of restaurants, the Walktrap algorithm.
+If the features extraction methods perform differently for the supervised and unsupervised approaches, we observe some very promising results.
+Theses insights could be used as the first step to an automated categorization system on the Yelp website.
 
@@
 \lettrine[nindent=0em,lines=1]{T}he classification system in Yelp is manual.
-When the owner of a business creates a page for his restaurant or bar, he is can provide a certain number of labels.
+When the owner of a business creates a page for his restaurant or bar, he can provide a certain number of labels.
 Yelp users can then alter or even add new tags based on their experiences.
 As part of the Yelp Data Set Challenge Round 6, we decided to tackle the issue of entries classification.
-Our ultimate objective is to create an automatised method to classify the businesses, based on their properties and most importantly on their reviews from Yelpers.
+Our ultimate objective is to create an automatised method to label the businesses, based on their properties and most importantly on their reviews from Yelpers.
+The new tags could be added to the existing tags to build a finer classification.
 \\
@@
 This project can be divided in three parts.
-First, to extract feature, we applied various dimensionality reduction methods such as Latent Dirichlet Allocation (LDA) or Non-negative Matrix Factorisation (NMF) to embed the reviews into a geometrical space.
-Then, we applied supervised learning methods to evaluate how relevant are the feature to predict the labels.
-Last, we built an unsupervised clustering method using the Walktrap algorithm.
+First, to extract the features, we applied various dimensionality reduction methods such as Latent Dirichlet Allocation (LDA) or Non-negative Matrix Factorization (NMF) to embed the reviews into a geometrical space.
+Then, we applied supervised learning methods to evaluate how much information the features carry.
+Last, we built an unsupervised clustering method using a community detection algorithm.
 
@@
 \noindent For simplicity, we chose to focus on restaurants and bars in the city of Las Vegas, Nevada.
-This reduced the data to a dataset of 3822 businesses, with about 20 thousands reviews and 250 other features per entry such as hours, parking availabity, take-out, ambience.
-If the numerical data provided by Yelp is mostly cleaned, it was not the case of the text data.
-Cleaning the reviews represented a significant part of this final project.
-We present some of the steps we followed in the process:\\
+This reduced the data to a dataset of 3 822 businesses, with about 20 thousands reviews and 250 other features per entry such as hours, parking availabity, take-out, ambience.
+If the numerical data provided by Yelp is mostly cleaned, it was not the case for the text data.
+Cleaning the reviews represented a significant part of this project.
+Here are some of the steps we followed in the process:\\
 
 \begin{compactitem}
-    \item We aggregated all the reviews about a particular business into a "super" review, in order to get a general sense of what the restaurant was about;
+    \item We aggregated all the reviews about a particular business into a "super" review, in order to get a general sense of what the restaurant was about (this was possible because we don't need to differentiate the users writing the reviews);
     \item We applied spelling corrections, removed common stopwords and generic words such as "table" or "restaurants";
-    \item We attempted at only selecting common words and not adjectives in order to focus on what the venues were about and not the users' opinions (this process was done taking advantage of Spark to reduce the computing time);
-    \item We transformed the corpus of "super reviews" into a document-term matrix that we could exploit;
+    \item We attempted at only selecting common words, removing the adjectives, in order to focus on what the venues were about and not the users' opinions (this process was done taking advantage of Spark to reduce the computing time);
+    \item We transformed the corpus of the "super reviews" into a document-term matrix that we could exploit;
     \item As we aggregated the reviews, some words may be more prevalent than others, so we scaled the words counts into the range [0, 100] for each review.
+(this step produced a finer words distribution for each topic of the LDA)
 \end{compactitem}
@@
 The motivation behind OVI is twofold.
-First, it appeared more appropriate to the data we were working with, indeed new reviews can always be added to the corpus in continuous flow.
-Second, it showed some extremely significant time improvement over the Gibbs sampler version in Python.
+First, it appeared more appropriate to the data we were working with.
+If some restaurants have already enough reviews to be classified accurately, most of them could have finer labels with more reviews.
+Moreover, some nuances may appear over the time among the clusters of restaurants.
+As a result, we should be able to add the new reviews to the corpus in a continuous flow.
+Second, it showed some extremely significant time improvements over the Gibbs sampler version in Python.
+Nonetheless, a major drawback of this method is the high sensitivity to the hyperparameters.
 We also wanted to compare the performance of LDA with a non-probabilistic approach which is the NMF.
@@
 \noindent This distribution is intractable.
-As mentioned above, we used two  methods to infer it: through a Gibbs sampler or variational inference.
-In the first case, we are estimating the hyper parameters $\theta$ and $\phi$ with samples on the different variables.
+As mentioned above, we used two  methods to infer it: with a Gibbs sampler and with variational inference.
+In the first case, we are estimating the hyperparameters $\theta$ and $\phi$ with samples on the different variables.
 Alternatively, we chose the online variational inference method which finds the variational parameters that optimize a lower bound on the loglikelihood.
 The setup \cite{OLLD} of the variational inference is as follows.
-We first approximate the true posterior by a simpler and factorised distribution:
+
+\noindent We first approximate the true posterior by a simpler and factorised distribution:
 
@@
 
-\noindent The $\boldsymbol{\gamma}$ parameter rule the topic assignments for each document and the $\boldsymbol{\lambda}$, the topics themselves.
+\noindent The $\boldsymbol{\gamma}$ parameter rules the topic assignments for each document and the $\boldsymbol{\lambda}$ the topics themselves.
 We then minimise the KL divergence between the distribution $q$ and the true posterior $p$.
@@
 
-\noindent where $\kappa \in (0.5,1]$ rules how fast we forget old values of $\tilde{\lambda}$ and $\tau_{0}$ how much weight one wants to put on the first iterations.
-$\alpha$ and $\eta$ where fixed at the same value $\frac{1}{|D|}$.
+\noindent where $\kappa \in (0.5,1]$ rules how fast we forget the old values of $\tilde{\lambda}$ and $\tau_{0}$ how much weight one wants to put on the first iterations.
+$\alpha$ and $\eta$ were fixed at the same value $\frac{1}{|D|}$.
 
@@
 The perplexity is defined as the geometric mean of the log likelihood of the words in the held-out set of documents given the trained model.
-In our case, for each document we held out 20\% of the words which constitue the validation set to apply a 5-fold cross-validation.
+In our case, for each document we held out 20\% of the words which constitute the validation set to apply a 5-fold cross-validation.
 
@@
 
-\noindent We used this measure to optimize the number of topics K and the hyper parameters $\kappa$, $\tau$ of the optimization.
+\noindent We used this measure to optimize the number of topics K and the hyperparameters $\kappa$, $\tau$ of the optimization.
 We also used the perplexity on the training set to benchmark our algorithm with the Gibbs sampler in the LDA 1.0.3 package in Python:
@@
 \noindent We obtained similar results using the NMF approach.
-The topics themselves were not our primary interested.
-As mentioned in the introduction, we were using these methods primarly for dimensional reduction purposes.
+As mentioned in the introduction, the topics themselves were not our primary interested, we were using these methods for dimensional reduction purposes.
 \\
@@
 We would like to make a general comment about the online variational algorithm.
-We noticed that its algorithm is extremely sensitive to the hyperparametrisation, i.e the batch size $S$, the forgetfullness parameter $\kappa$ and the early iterations weith parameter $\tau$.
+We noticed that its algorithm is extremely sensitive to the hyperparametrisation, i.e the batch size $S$, the forgetfullness parameter $\kappa$ and the early iterations weight parameter $\tau$.
 This was also noted by Tamara Broderick, Nicholas Boyd, Andre Wibisono and Ashia C.
 Wilson in their paper\cite{svi}.
-In addition to validating the number of topics, validating over these parameters was crucial to obtain valuable results.\\
+Validating the number of topics and these parameters was indeed crucial to obtain valuable results.\\
 
@@
 
-\noindent The features are divided into two main parts: on one hand, the topics assignements extracted from the reviews with the LDA and on the other hand, the properties provided by Yelp.
+\noindent The features are divided into two main parts: on one hand, the topics assignements extracted from the reviews with the topic modeling algorithm (LDA or NMF) and on the other hand, the properties provided by Yelp.
 Pre-processing the latter part provided a 198 dimensional vector.
@@
 
-\noindent Given our numerical features, many different discriminative and generative models could be appllied on our data.
+\noindent Given our numerical features, many discriminative and generative models could be applied on our data.
 Nonetheless, the indicator features are sparse and the data are really noisy.
-We therefore needed to consider a penalized or aggregated model to reduce overfitting.\\
+We therefore needed to consider a penalized and/or aggregated model to reduce the overfitting.\\
 
-\noindent We chose a one-vs-all approach to tackle this multi-label task, and built one binary classifier for each label.
-We then assign to the entries the labels predicted by each model.
+\noindent We chose a one-vs-all approach to tackle this multi-label task and built one binary classifier for each label.
+We then assigned to the entries the labels predicted by each model.
 The goal is here to explore how the different models perform and to tune them to come up with the best estimator.
@@
 
+In our experiments, we focused on the 10 most represented labels in the Las Vegas restaurants, which constitute our set of outputs.
+A same restaurant may have more than one label as we consider a multi-label classification.
+
 \paragraph{Dimensionality Reduction}
 
-\noindent We decided to reduce the dimension of the dataset before fitting our model.
+\noindent We decided to reduce the dimension of the second part of the dataset (the properties provided by Yelp) before fitting our model.
 As the high-dimensionality is largely due to the customer check-in counts and as they share a common structure, we decided to project them in an euclidean space.
-The combination of the embedded features with the latent features provided by the reviews is more consistent.
-We apply a principal component analysis (PCA) while keeping \textbf{95\%} of the variance which reduces the dimension from \textbf{168} to \textbf{19}.
+Combining these embedded features with those provided by the reviews produced then a more consistent dataset.
+This dimensionality reduction was done with a principal component analysis (PCA), keeping \textbf{95\%} of the variance which reduces the dimension from \textbf{168} to \textbf{19}.
 
@@
 
-\noindent Here we provide the different results we obtained from our models.
-We ran one-vs-one classifiers for the 10 different labels which are the most represented in the Las Vegas restaurants.
+\noindent Here we provide the different results we obtained with our models.
+We ran one-vs-one classifiers for the 10 labels.
 Then we evaluated for each classifier its accuracy and averaged them to get the evaluation metric printed in the table.
-We tested them on three different kinds of features provided by the reviews depending on the method used to build them.
-Then we ran each model on the PCA projection and on the raw data.
-We also show for comparaison the baseline model where we do not assign any label.
-This result is really high because of the skewness of the considered sample, among the 10 categories considered for 3822 restaurants the most represented (Fast Food) contains 553 entries and the least (American New) 280 entries.
+We also plotted the ROC curves for a specific model.
+
+\noindent We tested them on three different kinds of features provided by the reviews depending on the method used to build them (\textit{see the columns}).
+Then, for each model, we used both the raw features provided by Yelp and those embedded by the PCA projection (\textit{see the rows}).
+We also show for comparison the baseline model where we do not assign any label.
+This result is really high because of the skewness of the considered sample: among the 10 categories considered for 3 822 restaurants, the most represented (Fast Food) contains 553 entries and the least (American New) 280 entries.
 
@@
 With the Gibbs sampling approach, we approximate the true underlying distribution at each iteration to refine our estimator.
-As a result, the latter method is by nature better to find the best model as long as it has enough iteration to converge and there actually exists an underlying mixture models.
+As a result, the latter method is by nature better to find the best model as long as it has enough iterations to converge and there actually exists an underlying mixture models.
 Nevertheless, the OVI remains a good proxy with regard to its time execution (53s against 50min for the Gibbs Sampler).\\
@@
 \noindent If we then compare the models to each other, we see that the support vector machine performs poorly and that the linear version was even closer to the baseline.
-This confirms that the data is not linearly separable and even their projection by the rbf function used in sklearn library (gamma function) is quite impossible to separate.
+This confirms that the data are not linearly separable and even their projection by the rbf function used in sklearn library (gamma function) is quite impossible to separate.
 The logistic regression performs better under the l1 penalization because of the sparsity of our features.
 Lastly, the random forest managed to reduce the common overfitting of the decision trees while aggregating them and provides on the PCA projection a very good estimator.\\
-
-\noindent We plotted here the ROC curves of the Random forest for the 10 classes considered.
-The ranking with respect to the area under the curve is very close to the one induced by the number of positive elements for each class.This shows that the more positive elements we have, the better the model actually performs.
-Nonetheless, trying to learn the model on a smaller and more balanced train set for the classes with a low number of positive elements does not improve the classification accuracy.
 
@@
 
+\noindent We plotted here the ROC curves of the Random forest for the 10 classes considered.
+The ranking with respect to the area under the curve is very close to the one induced by the number of positive elements for each class.
+This shows that the more positive elements we have, the better the model actually performs.
+Nonetheless, learning the model on a smaller and more balanced train set with regards to the predicted class, i.e.
+with a lower number of negative elements, did not improve the classification accuracy.
+
 \paragraph{Feature Importance}
@@
 This provided an answer to two important questions: \textit{Are the feature extracted from the reviews more relevant than the one provided by Yelp to classify the restaurants by category?
-Among the features extracted by the review, can we identify for each category one or several highly discriminative features?} Moreover, we can compare the performance of the two different LDA we used.\\
+Among the features extracted by the reviews, can we identify for each category one or several highly discriminative features?} Moreover, we can compare the performance of the two different LDA we used.\\
 
@@
 We used the measure provided by scikit learn to evaluate the importance of the features.
-It is defined as the total decrease in node impurity averaged over all trees of the ensemble.
+It is defined as the total decrease in node impurity averaged over all the trees of the ensemble.
+
+\begin{figure}[H]
+\centering
+\includegraphics[width=1\linewidth]{img/gs_topics.png}
+\caption{Topics extracted from the Las Vegas reviews using GS}
+\end{figure}
 
@@
 
-\begin{figure}[H]
-\centering
-\includegraphics[width=1\linewidth]{img/gs_topics.png}
-\caption{Topics extracted from the Las Vegas reviews using GS}
-\end{figure}
-
 \noindent First, considering the results for the OVI features, we observe that some properties provided by Yelp are discriminative for our classification.
-For example, the attribute \textit{Good for Kids} helps to sort the Bars and the Nightlife categories which is not surprising.
+For example, the attribute \textit{Good for Kids} helps to sort the Bars and the Nightlife categories.
 The Fast Food may be the restaurants with the largest number of reviews as they have the largest number of customers, the model confirms this with the high weight on the \textit{reviews\_count}.
@@
 Now, if we consider the results for the GS features, each category has a highly discriminative feature.
-Moreover, if we look at the most common words for each of these topics in the figure 10, we naturally understand their importance in the classification.
+Moreover, if we look at the most common words for each of these topics in the figure 6, we naturally understand their importance in the classification.
 This result confirms our analysis on the models.
@@
 The weight of the most important feature and its difference with those of the other features are higher.
-We can explain this by the fact that the projection gave more structure to the data and reduces the noise.\\
+We can explain this by the fact that the projection gave more structure to the data and reduced the noise.\\
 
 \noindent This part was about confronting our data to supervised methods to grasp their patterns and also coming up with a good classification.
-We provided empirical results to confirm the difference between the two common LDA methods and proved that with the Gibbs sampling, the LDA can be really efficient at finding the underlying topics on a set of documents.
-It also proved that it performed much butter than a matrix factorization method.
-Related to our problem, it showed us that if numerical features provided by Yelp contained some information, the LDA features remained much more important when looking to find the labels of a restaurant.
+We provided empirical results to confirm the differences between the two common LDA methods and proved that with the Gibbs sampling, the LDA can be really efficient at finding the underlying topics on a set of documents.
+It also performed much better than a matrix factorization method.
+Related to our problem, this showed us that if the numerical features provided by Yelp contained some information, the LDA features remained much more important when looking for the labels of a restaurant.
 
@@
 To do so and in order to check if our classification attempt was successful, we sampled about 1000 restaurants having tags in the following list of 6 categories: Sushi, Steakhouse, Seafood, Mexican, Sports and Breakfast \& Brunch.
-We then applied applied the following methodology.\\
+We then applied the following methodology:\\
 
@@
 
-\noindent The choice of having a non-zero weight between two restaurants even though they are not "close" is motivated by the fact that many graph clustering algorithm, in particular the WalkTrap algorithms that we used, only work on a connected graph.\\
+\noindent The choice of having a non-zero weight between two restaurants even though they are not "close" is motivated by the fact that many graph clustering algorithm, in particular the WalkTrap, only work on a connected graph.\\
 
@@
 We ran the algorithm from the \emph{igraph} \cite{igr} package in R on the three graphs generated with the three approaches mentionned above (NMF, OVI LDA, GS LDA).
-The results where extremely similar.
+The results were extremely similar.
 We outputted a dendogram (cf.
-Annex) representing the obtained clustering.
+figure 12) representing the obtained clustering.
 We colored the tag of each business for a better readability.
@@
 It seems very unlikely to discover a restaurant that one can identify as both a Mexican and a Sushi place or even a Sushi place specialising in Breakfast (unless its speciality is the takagoyaki, a type of Japanese omelette made by "rolling together several layers of cooked egg").
-It was often the case that misclassified restaurants had the tag "Buffet" which is for our purpose of classification our worst ennemy as it will phagocytose many categories at once.
+It was often the case that misclassified restaurants had the tag "Buffet" which is for our purpose of classification our worst ennemy as it will stand for many categories at once.
 
@@
 
-So far, we managed to extract the categories of the restaurants as latent features with a latent dirichlet allocation algorithm on the aggregated reviews for each restaurant. \\
+So far, we managed to extract the categories of the restaurants as latent features with a Latent Dirichlet Allocation algorithm on the aggregated reviews for each restaurant. \\
 
-Futur work could focus on the sub-cliques and try to get a finer classification by combining them with other features like check-ins, parking availability, etc.
-As a variant, we could also try a supervised LDA, where we use the existing categories as a response variable associated with each document and infer the joint model of the documents and the responses.\\
-
-As a variant, we could try a supervised LDA, where we use the existing categories as a response variable associated with each document and infer the joint model of the documents and the responses.
-Lastly, this method is applicable on each review separately to predict the rating of the review, with a supervised lda also to avoid the predominance of the categories in the topics.
+Future work could focus on the sub-cliques and try to get a finer classification by combining them with other features like check-ins, parking availability, etc.
+As a variant, we could also try a supervised LDA, where we use the existing categories as a response variable associated with each document and infer the joint model of the documents and the responses.
+Lastly, as interpretability does not matter, we could try neural architectures to build the features.
 
@@
 
-This study illustrates different methods to extract feature from a set of documents.
-The results confirmed that the latent Dirichlet allocation manages to grasp the underlying features.
-The comparison with the supervised learning methods confirmed the importance of the feature extraction part in a machine learning problem.
+This study illustrates different methods to extract features from a set of documents.
+The results confirmed that the Latent Dirichlet Allocation manages to grasp the underlying features.
+The comparison with the supervised learning methods confirmed the importance of the features extraction part in a machine learning problem.
 It also corroborates the assumption that the features of the businesses could be used to infer their category labels.
 Finally, the unsupervised clustering process we developped provides encouraging results and could result in an automation tool for Yelp to label properly its database.
+
+\section*{Code}
+
+The code for this project can be found at the following address:
+
+\begin{center}
+www.github.com/nicodri/CS281
+\end{center}
 
